% ===========================================================================
% STANDARD OPERATING PROCEDURE — 22 Constance St Unit Trust
% Monthly Reporting Pack Preparation
% Version 2.4 — Revised February 2026
% ===========================================================================
\documentclass[11pt,a4paper,openany]{article}

% --- Fonts: Palatino (textbook-standard serif) + Helvetica (sans headings) ---
\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}
\usepackage{palatino}          % Palatino body text — classic textbook serif
\usepackage{mathpazo}          % Matching math font
\usepackage[scaled=0.92]{helvet} % Helvetica for sans-serif (headings, account codes)
\usepackage{microtype}         % Microtypography — improves text flow
\usepackage{setspace}          % Line spacing control

% --- Page Layout ---
\usepackage[top=2.8cm, bottom=2.8cm, left=2.8cm, right=2.8cm, headheight=26pt]{geometry}
\setstretch{1.15}              % Slightly opened line spacing for readability

% --- Structure & Navigation ---
\usepackage{titlesec}
\usepackage{titletoc}
\usepackage{enumitem}
\usepackage{parskip}

% --- Tables ---
\usepackage{booktabs}
\usepackage{longtable}
\usepackage{tabularx}
\usepackage{array}
\usepackage{multirow}
\usepackage{float}
\usepackage{caption}

% --- Visual ---
\usepackage{xcolor}
\usepackage{colortbl}
\usepackage{tcolorbox}
\tcbuselibrary{skins, breakable}
\usepackage{fancyhdr}
\usepackage{lastpage}
\usepackage{graphicx}
\usepackage{amsmath}
\usepackage{ragged2e}
\usepackage{calc}
\usepackage{hyperref}
\usepackage{xurl}
\usepackage{pdflscape}
% pdflscape (via lscape) calls \thispagestyle{empty} on every landscape page,
% suppressing headers/footers. Patch the internal macro to use fancy instead.
\makeatletter
\def\LS@makecol{\setbox\@outputbox\vbox{\pagestyle{fancy}\box\@outputbox}}
\makeatother
\usepackage{tikz}
\usetikzlibrary{shapes.geometric, arrows.meta, positioning, fit, backgrounds, calc}
\usepackage{rotating}
\usepackage{appendix}

% ===========================
% COLOUR PALETTE
% ===========================
\definecolor{navy}{HTML}{14284B}
\definecolor{steel}{HTML}{3B6B9C}
\definecolor{sky}{HTML}{D0E2F2}
\definecolor{palesky}{HTML}{EAF1F8}
\definecolor{warmgray}{HTML}{F6F5F3}
\definecolor{midgray}{HTML}{D8D8D8}
\definecolor{textgray}{HTML}{5A5A5A}
\definecolor{critred}{HTML}{B82E2E}
\definecolor{critbg}{HTML}{FDF0F0}
\definecolor{warnamber}{HTML}{C77C15}
\definecolor{warnbg}{HTML}{FEF8ED}
\definecolor{infoteal}{HTML}{1A7A6D}
\definecolor{infobg}{HTML}{EDF8F6}
\definecolor{contrabg}{HTML}{FFF8E7}
\definecolor{contraborder}{HTML}{D4A017}

% ===========================
% HYPERREF
% ===========================
\hypersetup{
    colorlinks=true,
    linkcolor=steel,
    urlcolor=steel,
    citecolor=steel,
    hypertexnames=false,
    pdftitle={SOP — Monthly Reporting Pack — 22 Constance St Unit Trust},
    pdfauthor={UFS Fund Accounting Team},
}

% ===========================
% SECTION HEADINGS (textbook style with sans-serif)
% ===========================
\titleformat{\section}
    {\Large\sffamily\bfseries\color{navy}}
    {\thesection}{0.8em}{}
    [\vspace{-0.3em}{\color{steel}\rule{\textwidth}{0.6pt}}]
\titleformat{\subsection}
    {\large\sffamily\bfseries\color{navy}}
    {\thesubsection}{0.7em}{}
\titleformat{\subsubsection}
    {\normalsize\sffamily\bfseries\color{steel}}
    {\thesubsubsection}{0.6em}{}

\titlespacing*{\section}{0pt}{2em}{1em}
\titlespacing*{\subsection}{0pt}{1.4em}{0.6em}
\titlespacing*{\subsubsection}{0pt}{1em}{0.4em}

% ===========================
% HEADER / FOOTER
% ===========================
\pagestyle{fancy}
\fancyhf{}
\fancyhead[L]{\small\sffamily\textcolor{navy}{\textbf{22 Constance St Unit Trust}}}
\fancyhead[R]{\small\sffamily\textcolor{textgray}{SOP --- Monthly Reporting Pack}}
\fancyfoot[L]{\small\sffamily\textcolor{textgray}{Confidential --- Internal Use Only}}
\fancyfoot[R]{\small\sffamily\textcolor{textgray}{Page \thepage\ of \pageref{LastPage}}}
\renewcommand{\headrulewidth}{0.4pt}
\renewcommand{\footrulewidth}{0.3pt}
\renewcommand{\headrule}{\hbox to\headwidth{\color{steel}\leaders\hrule height \headrulewidth\hfill}}
\renewcommand{\footrule}{\hbox to\headwidth{\color{midgray}\leaders\hrule height \footrulewidth\hfill}\vskip 2pt}

% ===========================
% CALLOUT BOXES (redesigned)
% ===========================
\newtcolorbox{critical}{
    enhanced, breakable,
    colback=critbg, colframe=critred,
    boxrule=0pt, leftrule=4pt,
    fonttitle=\sffamily\bfseries\color{critred},
    title={\small CRITICAL},
    top=5pt, bottom=5pt, left=8pt, right=8pt,
    before skip=10pt, after skip=10pt,
    sharp corners
}
\newtcolorbox{warning}{
    enhanced, breakable,
    colback=warnbg, colframe=warnamber,
    boxrule=0pt, leftrule=4pt,
    fonttitle=\sffamily\bfseries\color{warnamber},
    title={\small WARNING},
    top=5pt, bottom=5pt, left=8pt, right=8pt,
    before skip=10pt, after skip=10pt,
    sharp corners
}
\newtcolorbox{note}{
    enhanced, breakable,
    colback=infobg, colframe=infoteal,
    boxrule=0pt, leftrule=4pt,
    fonttitle=\sffamily\bfseries\color{infoteal},
    title={\small NOTE},
    top=5pt, bottom=5pt, left=8pt, right=8pt,
    before skip=10pt, after skip=10pt,
    sharp corners
}
\newtcolorbox{contradiction}{
    enhanced, breakable,
    colback=contrabg, colframe=contraborder,
    boxrule=0pt, leftrule=4pt,
    fonttitle=\sffamily\bfseries\color{contraborder},
    title={\small REVISION NOTE --- Contradiction Identified and Corrected},
    top=5pt, bottom=5pt, left=8pt, right=8pt,
    before skip=10pt, after skip=10pt,
    sharp corners
}

% ===========================
% CUSTOM COMMANDS
% ===========================
\newcolumntype{L}[1]{>{\raggedright\arraybackslash}p{#1}}
\newcolumntype{R}[1]{>{\raggedleft\arraybackslash}p{#1}}
\newcolumntype{C}[1]{>{\centering\arraybackslash}p{#1}}
\newcommand{\acct}[1]{\textsf{\textbf{#1}}}  % Account codes in sans-serif bold
\newcommand{\thead}[1]{\cellcolor{navy}\textcolor{white}{\sffamily\bfseries\small #1}}
\newcommand{\tabhead}{\rowcolor{navy}\color{white}\sffamily\bfseries\small}

% Caption styling
\captionsetup{font=small, labelfont={sf,bf,color=navy}, format=plain, skip=6pt}

% ============================================================================
\begin{document}

% ============================================================================
% TITLE PAGE
% ============================================================================
\begin{titlepage}
\thispagestyle{empty}

% Top decorative bar
\noindent\colorbox{navy}{\parbox{\textwidth}{\vspace{6pt}\hspace{12pt}\textcolor{white}{\sffamily\normalsize CONFIDENTIAL --- FOR INTERNAL USE ONLY}\vspace{6pt}}}

\vspace{0.9cm}

\begin{flushleft}
{\fontsize{30}{36}\selectfont\sffamily\bfseries\textcolor{navy}{Standard Operating\\Procedure}}\\[0.4cm]
{\fontsize{16}{20}\selectfont\sffamily\textcolor{steel}{Monthly Reporting Pack Preparation}}\\[0.9cm]

{\fontsize{13}{17}\selectfont\sffamily\textcolor{navy}{\textbf{22 Constance St Unit Trust}}}\\[0.15cm]
{\sffamily\textcolor{textgray}{Unlisted Unit Trust}}\\[0.8cm]

\textcolor{steel}{\rule{8cm}{0.5pt}}\\[0.7cm]

\renewcommand{\arraystretch}{1.25}
\begin{tabular}{@{}>{\sffamily\bfseries\color{navy}}l @{\hspace{1.2em}} >{\color{black}}l @{}}
ABN                 & 28 218 694 388 \\
TFN                 & 552 125 429 \\
Constitution Date   & 17 April 2019 \\
Trustee             & 22 Constance St Pty Ltd (wholly owned subsidiary of CPG) \\
Manager             & Centennial Property Group Pty Ltd (CPG), ACN 151 746 977 \\
Property            & 22--26A Constance Street, Fortitude Valley QLD 4006 \\
Accounting Period   & 1 July to 30 June \\
Document Owner      & UFS Fund Accounting Team \\
\end{tabular}
\end{flushleft}

\vspace{1.0cm}

% Key Personnel box
\noindent\colorbox{palesky}{\parbox{\dimexpr\textwidth-2\fboxsep}{%
\vspace{8pt}\hspace{8pt}
\begin{minipage}{\dimexpr\textwidth-2\fboxsep-16pt}
{\sffamily\bfseries\color{navy}\large Key Personnel}\\[4pt]
\renewcommand{\arraystretch}{1.2}
\begin{tabular}{@{}>{\sffamily\bfseries\color{steel}}l @{\hspace{1em}} l @{}}
Preparer (UFS)            & Anthony Tran \\
1st Reviewer (UFS)        & Pantea Asgari \\
2nd Reviewer (UFS)        & Sonya Beatriz \\
Key Client Coordinator    & Kim Tran \\
Client Contact (CPG)      & William Cassimatis --- wcassimatis@centennial.com.au \\
Client Contact (CPG)      & Ally Hill --- ahill@centennial.com.au \\
\end{tabular}
\end{minipage}
\vspace{8pt}}}


\end{titlepage}

% ============================================================================
% TABLE OF CONTENTS
% ============================================================================
% \pagestyle{empty} suppresses headers/footers on ALL TOC pages (not just the
% first), then \pagestyle{fancy} is restored. Arabic counter is reset to 1 so
% content pages are numbered sequentially with no overlap with TOC pages.
\pagestyle{empty}
\tableofcontents
\clearpage
\pagestyle{fancy}
\pagenumbering{arabic}
\setcounter{page}{1}



% ============================================================================
\section{Fund Background and Investment Overview}
\label{sec:background}
% ============================================================================

\subsection{Property Description}

22--26 Constance Street, Fortitude Valley is a character commercial office building comprising two adjoining structures. The smaller front building fronts Constance Street; the rear Sub Station (dating to 1928) has been converted into creative commercial space.

\begin{table}[H]
\centering\small\sffamily
\caption{Property summary as at 31 January 2026}
\begin{tabularx}{\textwidth}{@{}>{\bfseries}L{4.5cm} X@{}}
\rowcolor{navy}\textcolor{white}{\bfseries Attribute} & \textcolor{white}{\bfseries Detail} \\
\midrule
Total Lettable Area (NLA) & 2,592 sqm \\
\rowcolor{warmgray}
Total Land Area & 1,539 sqm \\
Acquisition Price & \$8.77M (\$10.8M inclusive of acquisition costs) \\
\rowcolor{warmgray}
Acquisition Date & 23 July 2019 \\
Acquisition \$/sqm & \$3,383 per sqm \\
\rowcolor{warmgray}
Initial Yield at Acquisition & 2.05\% \\
Market Yield at Acquisition & 11.02\% \\
\rowcolor{warmgray}
Most Recent Valuation & Independent valuation --- \$13,200,000 as at 31 December 2024 \\
IP Carrying Value & \$13,590,288 (31 January 2026) \\
\rowcolor{warmgray}
St George Loan & \$5,000,000 facility, 1.95\% p.a., matures 15 June 2026 \\
\bottomrule
\end{tabularx}
\end{table}

\begin{critical}
The St George loan matures on \textbf{15 June 2026}. Loan refinancing or sale of the asset must be resolved before maturity. Monitor loan status monthly and escalate to CPG if no written refinancing confirmation has been received.
\end{critical}

% --- 1.2 Lease Schedule ---
\subsection{Current Lease Schedule}
\label{sec:leases}

The following table summarises all current leases for the property. Total leased area is 692 sqm of 2,592 sqm NLA ($\sim$26.7\% occupancy).

\begin{table}[H]
\centering\small\sffamily
\caption{Current lease register as at January 2026}
\label{tab:leases}
\begin{tabularx}{\textwidth}{@{}L{2.8cm} C{1.1cm} R{1.6cm} R{1.6cm} L{3.8cm} L{1.5cm}@{}}
\rowcolor{navy}\textcolor{white}{\bfseries\sffamily Tenant} & \textcolor{white}{\bfseries\sffamily Area (sqm)} & \textcolor{white}{\bfseries\sffamily Rent (\$/mth)} & \textcolor{white}{\bfseries\sffamily Rent (\$/yr)} & \textcolor{white}{\bfseries\sffamily Term} & \textcolor{white}{\bfseries\sffamily Type} \\
\midrule
5Point Projects & 200 & 7,500 & 90,000 & 28 October 2024 -- 27 October 2027 & Gross \\
\rowcolor{warmgray}
Popgun Labs & 156 & 7,793 & 93,520 & 16 December 2024 -- 15 December 2026 & Net \\
Sony Music Ent. & 336 & 14,797 & 177,563 & Month-to-month & Semi-gross \\
\midrule
\textbf{Total} & \textbf{692} & \textbf{30,090} & \textbf{361,083} & & \\
\bottomrule
\end{tabularx}
\end{table}

\begin{table}[H]
\centering\small\sffamily
\caption{Lease concessions and charge schedule detail}
\label{tab:concessions}
\begin{tabularx}{\textwidth}{@{}L{2.8cm} L{4.5cm} R{2cm} L{4cm}@{}}
\rowcolor{navy}\textcolor{white}{\bfseries\sffamily Tenant} & \textcolor{white}{\bfseries\sffamily Charge Item} & \textcolor{white}{\bfseries\sffamily Amount (\$/yr)} & \textcolor{white}{\bfseries\sffamily Period} \\
\midrule
5Point Projects & Rent --- Office & 120,000 & 28 October 2024 -- 27 October 2026 \\
\rowcolor{warmgray}
5Point Projects & Concession --- Rent Free & $-$30,000 & 28 October 2025 -- 27 October 2026 \\
Popgun Labs & Rent --- Office & 115,920 & 16 December 2025 -- 15 December 2026 \\
\rowcolor{warmgray}
Popgun Labs & Concession --- Rent Free & $-$22,400 & 16 December 2024 -- 15 December 2026 \\
Sony Music & Rent --- Office & 177,563 & 1 March 2024 -- 28 February 2026 \\
\rowcolor{warmgray}
Sony Music & OGS --- Outgoing Recoveries & 46,393 & 1 July 2025 -- 30 June 2026 \\
\midrule
\multicolumn{2}{@{}l}{\textbf{Total annual concessions (rent-free)}} & \textbf{$-$52,400} & \textbf{= \$4,366.67/month} \\
\multicolumn{2}{@{}l}{\textbf{Total annual outgoings recovery}} & \textbf{46,393} & \textbf{= \$3,866.07/month} \\
\bottomrule
\end{tabularx}
\end{table}

\textbf{Security deposits:} 5Point Projects --- bank guarantee \$33,000; Popgun Labs --- bank guarantee \$61,600.

\begin{warning}
\textbf{Sony Music} is on a month-to-month holdover. The original lease expired 29 February 2024 and the current charge schedule ends 28 February 2026. This tenant represents 336 sqm (49\% of leased area) and 49\% of gross rental income. Any vacancy arising from Sony's departure would materially affect the fund's income and ICR covenant position. Monitor and escalate to CPG.
\end{warning}

\begin{note}
The lease concession amounts tie directly to the rent journal entries: total concessions of \$52,400 p.a.\ = \$4,366.67/month, recorded as \acct{71.02} Rental Abatement. Outgoings recovery of \$46,393 p.a.\ (Sony only) = \$3,866.07/month, recorded as \acct{71.01}. This confirms the lease data is consistent with the journal entry framework.
\end{note}

% --- 1.3 Fund Status ---
\subsection{Current Fund Status --- Asset Sale in Progress}
\label{sec:sale-status}

As at January 2026, the fund is actively pursuing the sale of the property. This introduces additional accounting and reporting considerations.

\subsubsection{Account 709 --- Deferred Cost of Sale}

Sale-related costs are accumulated as a balance sheet asset (not expensed) while the sale is active. Components at 31 January 2026:

\begin{itemize}[nosep]
    \item CBRE: Technical due diligence --- \$13,400.00
    \item MP Realty Trust: Marketing campaign --- \$15,306.36
    \item K\&L Gates: Legal fees --- \$17,846.47
    \item MP Realty Trust: Commission --- \$82,812.50
    \item \textbf{Total deferred cost of sale: \$133,731.53}
\end{itemize}

\subsubsection{Account 307 --- Aborted Sales Campaign Cost}

Costs from a previously aborted sales campaign were expensed through the P\&L. \$20,119.39 was recognised in July 2025.

\subsubsection{Upon Sale Completion}

All deferred costs of sale will be de-recognised from the balance sheet and recognised against the gain or loss on disposal.

\begin{warning}
Deferred cost of sale (\acct{709}) must be reviewed each month. Do not expense these items through the P\&L while the sale is active. Once the sale is either completed or formally abandoned, seek CPG direction on accounting treatment.
\end{warning}

% --- 1.4 Cyclone ---
\subsection{Cyclone Damage --- Insurance Claim and Remediation Capex}
\label{sec:insurance}

The property sustained significant cyclone damage. The following accounting treatment must be maintained consistently each reporting period.

\textbf{Insurance Claim Income.} Recognised in \acct{73.02}. Proceeds are received directly into \acct{680} --- St George by the insurer (Steadfast IRS / Vision Re Partners). YTD to January 2026: \$214,136.10, comprising: September 2025 (\$160,602.00), November 2025 (\$10,707.00), December 2025 (\$42,827.10).

\textbf{Remediation Capex.} All remediation works are capitalised to \acct{781.01} --- Property Improvements. Major items include: roof/ceiling repairs and asbestos removal (FHS --- multiple claims); Tenancy 1D balcony remediation; additional structural repairs (\$23,561 --- FHS, July 2025); fire detection system replacement --- Ampac Fire Finder (\$8,572 accrual June 2025; \$5,592 October 2025; \$2,980 December 2025); Handler Property Group project management (\$6,125.52, August 2025); FHS major progress claims (\$204,184 + \$26,741 + \$18,903.50, August 2025).

\begin{note}
Each month: (1) confirm insurance claim receipts credited to St George (\acct{680}) and record in \acct{73.02}; (2) capitalise all remediation works to \acct{781.01} on the Capex tab (payments via NAB); (3) update fair value disclosure once a new valuation is received. Do \textbf{not} net insurance claims against remediation capex, and do \textbf{not} confuse insurance premium expenses (NAB) with insurance claim receipts (St George).
\end{note}

% --- 1.5 Strategy ---
\subsection{Investment Strategy}
\label{sec:strategy}

\begin{enumerate}[nosep]
    \item Acquire a recently refurbished, majority-vacant character building at a significant discount to market value.
    \item Execute an aggressive leasing and marketing campaign to achieve full occupancy.
    \item Sell the fully leased asset or refinance with strong ICR and WALE metrics.
\end{enumerate}


The fund is currently in the sale process notwithstanding that full occupancy has not been achieved. The sale is being pursued in the context of the approaching St George loan maturity (15 June 2026).

% --- 1.6 Fees ---
\subsection{Fee Structure}
\label{sec:mgmtfee}

\begin{table}[H]
\centering\small\sffamily
\caption{Fund fee structure}
\begin{tabularx}{\textwidth}{@{}>{\bfseries}L{4.5cm} X@{}}
\rowcolor{navy}\textcolor{white}{\bfseries Fee Type} & \textcolor{white}{\bfseries Basis} \\
\midrule
Acquisition Fee & 2\% of Gross Asset Value (GAV) \\
\rowcolor{warmgray}
Disposal Fee & 1\% of GAV \\
Annual Management Fee & 5\% of net receivable income (see note below) \\
\rowcolor{warmgray}
Performance Fee (Tier 1) & 20\% of all returns above 8\% IRR \\
Performance Fee (Tier 2) & 40\% of all returns above 15\% IRR \\
\bottomrule
\end{tabularx}
\end{table}



% ============================================================================
\section{Bank Accounts and Cash Structure}
\label{sec:banking}
% ============================================================================

\begin{critical}
The trust's primary operating bank is \textbf{NAB}, which processes all property-level income and expenses. The St George account (\acct{680}) is the lending facility; St George Bank debits interest charges and line fees directly from this facility account. It also receives insurance claim proceeds (credited directly by the insurer) and holds the \$1,325,000 sale deposit. No property operating transactions (rent, opex) are processed through St George.
\end{critical}

\subsection{Account Register}

\begin{table}[H]
\centering\small\sffamily
\caption{Bank account register}
\begin{tabularx}{\textwidth}{@{}L{2.8cm} X@{}}
\rowcolor{navy}\textcolor{white}{\bfseries\sffamily Account} & \textcolor{white}{\bfseries\sffamily Description} \\
\midrule
\acct{680} --- St George & St George Bank lending facility. \$5,000,000 drawn at 1.95\% p.a.; matures 15 June 2026. Interest charges and line fees are debited directly from this facility account by St George Bank (they do \emph{not} flow through NAB). Also receives insurance claim proceeds from insurer (Steadfast IRS / Vision Re Partners) and holds the \$1,325,000 sale deposit (matched by \acct{884} liability). No ordinary property operating transactions are processed through St George. \\
\rowcolor{warmgray}
\acct{685} --- NAB & NAB operating account. Receives all rent remittances and processes all property-level and trust-level expenses. Balance at 31 Jan 2026: \$71,714.32. \\
\acct{686} --- STA QLD & State-managed trust account (Queensland). CPG inter-entity transfers. Balance at 31 Jan 2026: nil. \\
\bottomrule
\end{tabularx}
\end{table}

\subsection{Cash Reconciliation Requirements}

\begin{enumerate}[nosep]
    \item \acct{680} (St George): Reconcile per bank statement to per balance sheet. Zero difference expected.
    \item \acct{685} (NAB): Reconcile per NAB bank statement to per balance sheet. Zero difference expected.
    \item \acct{686} (STA QLD): Reconcile per Yardi TB to per balance sheet.
    \item All reconciliations are performed in the \textbf{Cash} tab.
    \item The \textbf{Yardi vs.\ Bank Stat Rec} tab provides detailed NAB bank statement line-by-line reconciliation against the Yardi GL. All timing differences must be documented with narrative comments.
\end{enumerate}

% ============================================================================
\section{Yardi Trial Balance Import Process}
\label{sec:yardi}
% ============================================================================

\subsection{Overview}

Yardi is the property management and accounting system used by CPG. At period end, the Preparer downloads two trial balance movement exports from Yardi: \texttt{cs4001} (property-level accounts) and \texttt{22chts} (trust-level accounts) for 22 Constance Street. These exports are imported into the \textbf{Import\_Yardi} tab.

\subsection{Import Process}

\begin{enumerate}[nosep]
    \item The Preparer downloads the Yardi TB movement reports from Yardi: \texttt{cs4001} (property-level) and \texttt{22chts} (trust-level), both in TRNS/SPL/ENDTRNS format.
    \item The Preparer imports the data into the \textbf{Import\_Yardi} tab, which feeds \textbf{Yardi\_TB} and \textbf{Yardi\_Income Statement} tabs.
    \item The data is posted as a general journal (memo: ``Yardi import''), creating movements across accounts including: \acct{685} --- NAB, \acct{686} --- STA QLD, \acct{703} --- Deferred Income, \acct{706/707} --- Prepayments (Operating \& Insurance), \acct{71} --- Rental Income, \acct{700} --- Property Operating Expenses, \acct{882.02} --- Accrued Operating, and \acct{255} --- GST.
    \item The Preparer reconciles the Yardi TB to the reporting pack TB. The \textbf{TB} tab consolidates the Yardi import with UFS manual journals.
    \item The \textbf{Yardi vs.\ Bank Stat Rec} tab reconciles the NAB bank statement against Yardi GL movements.
\end{enumerate}

\subsection{Reconciliation Codes --- Yardi vs.\ Bank Statement}

The following five timing-difference cases govern both the Yardi~vs.\ Bank Statement reconciliation (Step~2, Section~\ref{sec:yardi-rec}) and the NAB cut-off entries (Phase~2, Step~3, Section~\ref{sec:cutoff}). The same classification is used throughout to ensure consistency.

\begin{table}[H]
\centering\small\sffamily
\caption{Timing difference classification codes (five cases)}
\label{tab:fivecases}
\begin{tabularx}{\textwidth}{@{}C{0.8cm} L{5.5cm} X@{}}
\thead{Case} & \thead{Condition} & \thead{Treatment} \\
\midrule
1 & Transaction in current period Yardi TB \textbf{matches} transaction in current period bank statement & No timing difference. Imported via Step~5 (Section~\ref{sec:yardi-import}). No Sundry Debtor entry required. \\
\rowcolor{warmgray}
2 & Transaction in \textbf{previous period} Yardi TB (\acct{NAB}) matches transaction in \textbf{current period} bank statement & DR \acct{685} --- NAB \quad CR \acct{Sundry Debtor}. \\
3 & Transaction in \textbf{next period} Yardi TB (\acct{NAB}) matches transaction in \textbf{current period} bank statement & DR \acct{Sundry Debtor} \quad CR \acct{685} --- NAB. \\
\rowcolor{warmgray}
4 & Transaction on bank statement does \textbf{not match} any transaction in previous, current, or next period Yardi TB & Request bank information from CPG. Post manual entries based on the nature identified once clarified. \\
5 & Transaction in current period Yardi TB does \textbf{not match} current or previous period bank statement & Record as Sundry Debtor (DR or CR as applicable) and await the next period bank statement. If aging is unreasonably long, request the nature from CPG. \\
\bottomrule
\end{tabularx}
\end{table}

Each reconciling item must be coded with a case number and narrative. The reconciliation must balance to zero for the period to be complete.

% ============================================================================
\section{Reporting Pack Workbook Structure}
\label{sec:workbook}
% ============================================================================

The reporting pack is maintained in an Excel workbook. Principal tabs:

{\small\sffamily
\begin{longtable}{@{}L{3.2cm} L{5cm} L{5.5cm}@{}}
\caption{Reporting pack tab reference}\\
\rowcolor{navy}\textcolor{white}{\bfseries Tab Name} & \textcolor{white}{\bfseries Purpose} & \textcolor{white}{\bfseries Key Inputs} \\
\midrule
\endfirsthead
\rowcolor{navy}\textcolor{white}{\bfseries Tab Name} & \textcolor{white}{\bfseries Purpose} & \textcolor{white}{\bfseries Key Inputs} \\
\midrule
\endhead
\bottomrule
\endfoot

Import\_Yardi & Raw Yardi GL import (TRNS/SPL) & Source for TB, PL, BS \\
\rowcolor{warmgray}
Cover Page & Summary cover for CPG distribution & ABN, TFN, Dashboard \& NAV links \\
CPG Dashboard & Executive dashboard for Fund Month End Meeting & P\&L, BS, unit price, capex, fees \\
\rowcolor{warmgray}
NAV per unit & Net Asset Value per unit & NTA adjusted/unadjusted (11,438,500 units) \\
Tax reconciliation & Tax income reconciliation & Taxable income, deferred, capital return \\
\rowcolor{warmgray}
STI calc / STI Adj & Lease incentive amortisation & Feeds PL leasing fee line \\
Sec.\ 40--880 / 25--25 & Tax deduction schedules & Input to tax reconciliation \\
\rowcolor{warmgray}
Tax depreciation & Depreciation schedule (tax) & Input to tax reconciliation \\
Cost base \& carrying value & Investment cost base tracking & Disposal calcs, CGT \\
\rowcolor{warmgray}
PL / BS / CFS & Financial statements & TB, accruals, prepayments, journals \\
TB & Trial Balance (Yardi + UFS) & Import\_Yardi + manual entries \\
\rowcolor{warmgray}
COA & Chart of Accounts reference & Account mapping \\
Yardi vs.\ Bank Stat Rec & NAB Yardi GL vs.\ bank statement & NAB bank statement \\
\rowcolor{warmgray}
GL & General Ledger detail & Yardi import, manual entries \\
Cash & Cash reconciliation (\acct{680}, \acct{685}, \acct{686}) & Bank statements, Yardi TB \\
\rowcolor{warmgray}
Receivables & \acct{662}, \acct{660}, \acct{709} & NAB report; sale cost tracking \\
Capex & Capex log (\acct{781.01}, \acct{781.02}) & Cyclone remediation, fire system \\
\rowcolor{warmgray}
Prepaid leasing fee & Leasing fee amortisation (\acct{706.07}, \acct{780.12}) & STI calc, CPG invoices \\
Prepayments\_operating & Operating prepayments (\acct{706.01}--\acct{706.07}) & Land tax, rates, insurance \\
\rowcolor{warmgray}
Borrowing cost prepaid & Borrowing cost amortisation (\acct{708.03}, \acct{708.04}) & St George loan costs \\
Payables & Trade payables (\acct{883}) and accruals & CPG invoices, NAB report \\
\rowcolor{warmgray}
Loan\_St George & Loan balance and interest & \$5M @ 1.95\%; maturity 15 Jun 2026 \\
\rowcolor{warmgray}
Accruals / Detailed Accruals & Monthly accruals (\acct{882.02}, \acct{882.16}) & NAB report, CPG invoices \\
Unitholders & Register and equity ledger & \$11,438,500 capital, distributions \\
\rowcolor{warmgray}
BAS\_Qtr / GST ledger & Quarterly BAS and GST workings & PL, invoices \\
\end{longtable}
}

% ============================================================================
\section{Monthly Reporting Process}
\label{sec:process}
% ============================================================================

The monthly reporting cycle follows three sequential phases comprising ten procedural steps.


\begin{table}[H]
\centering\small\sffamily
\caption{Monthly reporting timeline}
\begin{tabularx}{\textwidth}{@{}C{0.7cm} L{2.5cm} X L{2.2cm}@{}}
\rowcolor{navy}\textcolor{white}{\bfseries\sffamily Step} & \textcolor{white}{\bfseries\sffamily Responsible} & \textcolor{white}{\bfseries\sffamily Action} & \textcolor{white}{\bfseries\sffamily Timing} \\
\midrule
\multicolumn{4}{@{}l}{\textit{\textbf{Phase 1 --- Source Documents, Reconciliation and TB Import}}} \\
\midrule
1 & CPG & Uploads St George bank statement, bank information responses, and supporting invoices to SharePoint. & BD1 \\
\rowcolor{warmgray}
2 & Client Coordinator & Downloads NAB bank statement; archives in UFS Shared Folder. & 20th \& BD1 \\
3 & Preparer & Downloads Yardi TB (\texttt{cs4001} and \texttt{22chts}) from Yardi. Downloads St George bank statement from SharePoint. Reconciles Yardi NAB TB vs.\ NAB bank statement. & 20th \& BD1 \\
\rowcolor{warmgray}
4 & Preparer & Submits bank information request to CPG; follows up unidentified items. & 20th \& BD1 \\
5 & CPG & Provides bank information responses and uploads supporting invoices to SharePoint. & 20th \& BD1 \\
\rowcolor{warmgray}
6 & Preparer & Revises Yardi TB (trust-level and sale/leasing reclassifications); imports revised TB. & BD1 \\
\midrule
\multicolumn{4}{@{}l}{\textit{\textbf{Phase 2 --- Reporting Pack Compilation}}} \\
\midrule
7 & Preparer & Compiles all tabs: property level, trust level, NAV, dashboard, distribution workings. Records insurance claim income and cyclone capex. & BD2--BD4 \\
\midrule
\multicolumn{4}{@{}l}{\textit{\textbf{Phase 3 --- Internal Review and Client Distribution}}} \\
\midrule
\rowcolor{warmgray}
8 & Preparer & Sends pack to 1st and 2nd Reviewer; clears all comments. & BD4 \\
9 & 1st/2nd Reviewer & Reviews and signs off checklists (NAV, BAS, Distribution). & BD5 \\
\rowcolor{warmgray}
10 & 1st Reviewer & Sends approved NAV pack and monthly report to CPG. & BD5 \\
\bottomrule
\end{tabularx}
\end{table}

% ============================================================================
\section{Phase 1: Source Documents, Reconciliation and TB Import}
\label{sec:phase1}
% ============================================================================

Phase 1 covers all preparatory work before reporting pack compilation: collecting source documents, reconciling the Yardi NAB trial balance against the NAB bank statement, submitting the bank information request to CPG, revising the Yardi TB, and importing the revised TB. Steps must be completed in sequence --- the Preparer reconciles the NAB bank statement against the Yardi TB \emph{before} revising and importing the TB. All Phase~1 work is completed before Phase~2 (Section~\ref{sec:phase2}) begins.

\subsection{Step 1 --- Collect Source Documents}

\subsubsection{Property-Level Source Documents (NAB)}

The Key Client Coordinator downloads the NAB bank statement and archives it in the UFS Shared Folder. The NAB bank statement covers all property-level cash transactions including: rental income remittances (commercial rent, outgoings recovery); fund administration expenses; development costs and cyclone remediation capex payments; professional expenses (legal, valuation, consulting); insurance premium expenses; and all property operating expenses (Handler Holdings --- property management; Energy Australia --- electricity; Office of State Revenue --- land tax; council rates; Queensland Urban Utilities --- water; Grolife --- garden maintenance; Premier Fire --- fire safety; AJT Prestige / JJ Waste --- cleaning; security fees; leasing commissions).

\begin{note}
Insurance premium \emph{expenses} are paid via NAB (\acct{685}). Insurance claim \emph{proceeds} are received into St George (\acct{680}) directly from the insurer --- these do not appear on the NAB bank statement.
\end{note}

\subsubsection{Trust-Level Source Documents (NAB and St George)}

Trust-level cash transactions on NAB include: BAS payments; distribution payments; CPG STA QLD transfers; BPAY payments; and sale commission payments (MP Realty Trust).

St George bank statement covers: interest and line fee payments (debited from the facility); insurance claim proceeds credited by insurer (Steadfast IRS / Vision Re Partners); and the \$1,325,000 sale deposit received.

CPG uploads the St George bank statement to SharePoint. The Preparer downloads it from SharePoint as needed for reconciliation.

\subsubsection{Trust-Level Expense Accounts (Accruals --- Non-Cash)}
\label{sec:trust-accrual-accounts}

Trust-level expenses are \textbf{not processed through any bank account}. They are posted as manual accrual journals to \acct{882.16} --- Fund Accruals (Balance Sheet liability) each period. This is distinct from property-level operating accruals (\acct{882.02}) which are imported via the Yardi TB.

\textbf{Three primary source locations} must be checked each period to support these accruals:

\begin{enumerate}[nosep]
    \item \textbf{St George (CPG-managed bank):} The St George bank statement (downloaded from CPG SharePoint) is the \textbf{primary evidence} for interest and line fee charges. Both are debited directly from the St George facility account (\acct{680}) by St George Bank --- they do \emph{not} appear on the NAB bank statement and are \emph{not} paid via NAB. The St George statement confirms the exact debit dates and amounts for \acct{303.01} (Loan Interest) and \acct{303.02} (Line Fees). \textbf{Both are recorded on a cash basis:} the entry is posted directly when St George debits the facility --- DR \acct{303.01} / CR \acct{680} for interest and DR \acct{303.02} / CR \acct{680} for line fees. No month-end accrual is raised for either item.

    \item \textbf{NAB (Key Client Coordinator):} The NAB bank statement (archived in UFS Shared Folder by the Key Client Coordinator) confirms cash payments for trust-level costs such as BAS, distribution, and BPAY payments. Management fee and admin fee payments may also appear here when settled. NAB entries confirm settlement of previously accrued liabilities in \acct{882.16}.

    \item \textbf{Yardi (CPG-managed accounting system):} CPG records certain trust-level charges in Yardi (e.g.\ management fees, fund admin fees). The Yardi TB export (\texttt{22chts} --- trust-level code) will show these as P\&L charges. Per the SOP procedure (Step~4, Section~\ref{sec:yardi-revise}), these are \emph{reclassified} from the Yardi P\&L to \acct{882.16} during the Yardi TB revision process. The Preparer must identify and reclassify each trust-level item before import.
\end{enumerate}

\textbf{Other supporting sources for accrual estimation:} Where a current invoice or Yardi entry is not yet available, accruals may be estimated from:
\begin{itemize}[nosep]
    \item \textbf{Contracts and engagement letters:} Fixed-fee arrangements (e.g.\ UFS fund admin \$1,250/month, audit fee schedule) are accrued monthly based on the agreed contractual amount.
    \item \textbf{Prior period patterns:} Where invoices are periodic or irregular (e.g.\ ASIC fees, registry fees, consultant fees), prior period amounts and timing provide the best estimate. Document the basis used in the accrual workpaper.
    \item \textbf{CPG invoice or instruction:} Management fees (\acct{301.01}) are accrued at 5\% of net receivable income, or per CPG invoice if one has been issued for the period.
\end{itemize}

\textbf{Trust-level expense accounts accrued to \acct{882.16}:}

\begin{table}[H]
\centering\small\sffamily
\caption{Trust-level expense accounts (303.01 and 303.02 on cash basis; all others accrued to \acct{882.16})}
\begin{tabularx}{\textwidth}{@{}L{2.5cm} L{3.5cm} L{2.5cm} X@{}}
\rowcolor{navy}\textcolor{white}{\bfseries Account} & \textcolor{white}{\bfseries Description} & \textcolor{white}{\bfseries Primary Source} & \textcolor{white}{\bfseries Basis / Notes} \\
\midrule
\acct{301.01} & Management Fees & Yardi (\texttt{22chts}) / CPG invoice & 5\% of net receivable income; reclassify from Yardi P\&L to \acct{882.16} \\
\rowcolor{warmgray}
\acct{301.02} & Fund Admin \& Tax Fees & Contract (UFS) & UFS fixed fee \$1,250/month; no CPI increase applied over the engagement \\
\acct{301.03} & Registry Fees & Invoice (CPG SharePoint) & Per invoice; if not received, estimate from prior period pattern \\
\rowcolor{warmgray}
\acct{301.04} & Disposal Fee & CPG confirmation (conditional) & 1\% of GAV; accrue only upon CPG confirmation --- see note below \\
\acct{301.05} & ASIC Fee & ASIC notice / prior pattern & Annual; accrue monthly or in full at year-end \\
\rowcolor{warmgray}
\acct{301.10} & Other Expenses & Various & Miscellaneous trust-level costs not otherwise classified \\
\acct{302.02} & Legal Fee & Invoice (CPG SharePoint) & Trust-level legal costs only --- sale-related legal fees go to \acct{709} \\
\rowcolor{warmgray}
\acct{302.03} & Valuation Fee & Invoice (CPG SharePoint) & Independent valuation costs \\
\acct{302.04} & Consultant Fee & Invoice / CPG instruction & Per engagement letter or CPG direction \\
\rowcolor{warmgray}
\acct{302.05} & Audit Fee & Contract / prior pattern & Annual audit; accrue monthly or at period end \\
\acct{303.01} & Loan Interest & St George statement / Loan\_St George tab & \textbf{Cash basis} --- DR \acct{303.01} / CR \acct{680} when St George debits the facility. No month-end accrual to \acct{882.16}. \\
\rowcolor{warmgray}
\acct{303.02} & Line Fees & St George statement / facility schedule & \textbf{Cash basis} --- DR \acct{303.02} / CR \acct{680} when St George debits the facility. No month-end accrual to \acct{882.16}. \\
\acct{303.03} & Establishment Fee Amort. & Borrowing cost prepaid tab & Straight-line over remaining facility term \\
\rowcolor{warmgray}
\acct{303.04} & Legal Fee Amort. & Borrowing cost prepaid tab & Straight-line over remaining facility term \\
\acct{303.05} & Performance Fee & CPG confirmation (conditional) & Tier 1/Tier 2 structure; accrue only when threshold is probable --- see note below \\
\bottomrule
\end{tabularx}
\end{table}

\begin{note}
\textbf{Disposal Fee (\acct{301.04}) and Performance Fee (\acct{303.05}):} These account numbers are \emph{reserved} in the Chart of Accounts because both fees are expected to be triggered upon completion of the property sale. Neither is currently being accrued. Do not post to these accounts without explicit CPG confirmation. Do not post property-level operating accruals to \acct{882.16}; those belong to \acct{882.02}.
\end{note}

\subsubsection{Yardi TB Export}

The Preparer downloads the Yardi TB movement export directly from the Yardi system. Two separate exports are required each period:

\begin{itemize}[nosep]
    \item \textbf{Property-level} (code: \texttt{cs4001}): Covers rental income, operating expenses, prepayments, receivables, and property-level accruals.
    \item \textbf{Trust-level} (code: \texttt{22chts}): Covers management fees, professional fees, fund administration charges, and trust-level transactions.
\end{itemize}

Both exports are held temporarily before revision (Step~4, Section~\ref{sec:yardi-revise}) and import (Step~5, Section~\ref{sec:yardi-import}).

\subsubsection{Document Archiving}

Source documents are stored across \textbf{three} locations, each managed by a different party:

\begin{enumerate}[nosep]
    \item \textbf{UFS Shared Folder (UFS-managed):} The Key Client Coordinator downloads the NAB bank statement and archives it directly in the Trust's Shared Folder on the UFS internal network drive. This is the primary repository for UFS working files and the NAB bank statement.

    \item \textbf{CPG SharePoint (CPG-managed):} CPG uploads the following to the designated SharePoint location:
    \begin{itemize}[nosep]
        \item St George bank statement;
        \item Bank information request responses (explanations of unidentified NAB transactions);
        \item Supporting invoices corresponding to bank information requests (remediation invoices from FHS, Premier Fire, etc.; insurance remittance advices from Steadfast IRS / Vision Re Partners; sale-related invoices from CBRE, K\&L Gates, MP Realty Trust).
    \end{itemize}
    The Preparer accesses SharePoint to download these documents as needed for reconciliation and journal entry support.

    \item \textbf{Yardi (CPG-managed):} The Preparer downloads the Yardi TB movement export directly from the Yardi system. Two property codes are used:
    \begin{itemize}[nosep]
        \item \texttt{cs4001} --- Property-level accounts (rental income, operating expenses, prepayments, receivables);
        \item \texttt{22chts} --- Trust-level accounts (management fees, professional fees, fund administration).
    \end{itemize}
    Invoices and supporting documents attached to Yardi transactions are also accessible within the Yardi system.
\end{enumerate}

\begin{note}
Each location serves a distinct purpose: the UFS Shared Folder holds the NAB bank statement and UFS working files; CPG SharePoint holds the St George bank statement, bank information responses, and CPG-sourced invoices; Yardi holds the trial balance exports and attached invoices. All three locations must be checked each period to ensure completeness of source documentation.
\end{note}

\subsection{Step 2 --- Reconcile Yardi NAB TB vs.\ NAB Bank Statement}
\label{sec:yardi-rec}

Before revising or importing the Yardi TB, the Preparer reconciles the Yardi NAB trial balance against the NAB bank statement in the \textbf{Yardi vs.\ Bank Stat Rec} tab. This identifies all timing differences between Yardi and the bank, which are coded using the five-case classification (Table~\ref{tab:fivecases}) and documented with narrative. The reconciliation must balance to zero before proceeding.

\subsection{Step 3 --- Bank Information Request}
\label{sec:bankreq}

After completing the initial reconciliation, the Preparer submits a bank information request to CPG covering all unidentified or unmatched transactions from the NAB bank statement. Queries are documented in the bank information request template (Excel), covering: missing invoices, unidentified payments, cut-off items, and insurance claim remittance details.

The request is submitted twice: on the 20th of the current month and on BD1 of the following month. CPG uploads responses and supporting invoices to SharePoint between the 20th and BD1. The Preparer downloads these from SharePoint.

Additional requests for the sale and cyclone context:
\begin{itemize}[nosep]
    \item \textbf{Cyclone remediation:} New invoices/progress claims from FHS, Premier Fire, etc.\ Confirm insurance claim amounts from Steadfast IRS / Vision Re Partners.
    \item \textbf{Asset sale:} Updated deferred cost of sale invoices (CBRE, K\&L Gates, MP Realty Trust). Confirm sale exchange/settlement dates.
    \item \textbf{Loan maturity:} Confirm whether the St George facility has been formally extended or refinancing is in progress.
\end{itemize}

\subsection{Step 4 --- Revise Yardi TB}
\label{sec:yardi-revise}

Once the bank information request is submitted and CPG responses received (or best available), the Preparer reviews and revises the raw Yardi TB for two categories of adjustments. Revisions are documented in the \textbf{Yardi\_TB} tab before import.

\subsubsection{Trust-Level Expenses --- Reclassify from P\&L to BS Accrual}

Yardi records all expenses in the P\&L and only accrues property-level (operating) expenses. It does not accrue Trust-level expenses. Our procedure requires Trust-level expenses to be held in \acct{882.16} (Fund Accruals --- BS) until paid.

\textbf{Action:} Identify all Trust-level expense items in the Yardi TB recorded as P\&L charges. Reverse these from the Yardi P\&L and reclassify to \acct{882.16}. The accrual is cleared when the actual payment is made. Property-level operating expense accruals (\acct{882.02}) remain as recorded by Yardi.

\begin{note}
Trust-level expenses subject to reclassification include: management fees, fund admin fees, registry fees, ASIC fees, legal fees (trust-level), valuation fees, consultant fees, audit fees, and any conditional disposal/performance fees. Property-level operating expenses (council rates, insurance premiums, property management) stay in the P\&L.
\end{note}

\subsubsection{Sale-Related and Leasing Expenses --- Reclassify from P\&L to BS}

Invoices recorded by Yardi as operating expenses must be reviewed to determine their nature. The reclassification rules are:

\begin{enumerate}[nosep,leftmargin=*]
    \item \textbf{Invoice relates to the sale of the property} (e.g.\ commission, legal fee, advertising for sale): \\
    Reclassify from P\&L to \acct{709} --- Deferred Cost of Sale (BS asset). Do \emph{not} expense while the sale is active. Upon settlement, \acct{709} is de-recognised against the gain/loss on disposal.

    \item \textbf{Invoice relates to leasing} (e.g.\ leasing commission, tenant incentive, leasing agent fee): \\
    Reclassify from P\&L to \acct{780.12} --- Prepaid Leasing Fee (BS asset). At the same time, record the following contra entry to reflect the increase in investment property carrying value: DR \acct{780.30} --- Fair Value Adjustment / CR \acct{213} --- Gain/(Loss) on Revaluation.

    The leasing fee is then amortised monthly: DR \acct{700.26} --- Leasing Fee (P\&L) / CR \acct{780.12} --- Prepaid Leasing Fee. At each amortisation, simultaneously reverse the fair value entry: DR \acct{213} --- Gain/(Loss) on Revaluation / CR \acct{780.30} --- Fair Value Adjustment, so that the P\&L amortisation charge does not distort the fair value carrying amount.

    Net effect over the life of the leasing fee:
    \begin{itemize}[nosep]
        \item \acct{780.12} increases on capitalisation, decreases on amortisation --- nets to zero at end.
        \item \acct{780.30} increases on capitalisation, reverses on amortisation --- mirrors \acct{780.12} as its contra.
        \item \acct{213} (Gain/(Loss) on Revaluation) is credited on capitalisation, debited on amortisation --- net equity impact is zero over the period.
        \item \acct{700.26} (Leasing Fee) captures the periodic P\&L expense.
    \end{itemize}

    \item \textbf{Otherwise} (ordinary operating expense, not sale- or leasing-related): \\
    Leave as a normal operating expense in the P\&L --- no reclassification required.
\end{enumerate}

\begin{warning}
The classification of invoices as sale-related, leasing-related, or ordinary operating is critical and affects both the P\&L and balance sheet. Refer to the invoice description, supplier name, and CPG instruction. When in doubt, request CPG confirmation before posting.
\end{warning}

\subsection{Step 5 --- Import Revised Yardi TB}
\label{sec:yardi-import}

After completing all revisions in Step~4 (Section~\ref{sec:yardi-revise}), the Preparer imports the revised Yardi TB into the \textbf{Import\_Yardi} tab following the process in Section~\ref{sec:yardi}. The import creates movements in all relevant accounts including: \acct{685} --- NAB, \acct{686} --- STA QLD, \acct{703} --- Deferred Income, \acct{706/707} --- Prepayments (Operating \& Insurance), \acct{71} --- Rental Income, \acct{700} --- Property Operating Expenses, \acct{882.02} --- Accrued Operating, and \acct{255} --- GST. The revised TB (post-reclassification) forms the base from which all UFS manual journals are layered in Phase~2 (Section~\ref{sec:phase2}).

% ============================================================================
\section{Phase 2: Reporting Pack Compilation}
\label{sec:phase2}
% ============================================================================

Phase~2 compiles the reporting pack using the imported Yardi TB (Phase~1) as its foundation. The subsections below follow the recommended completion order: property-level entries first, then bank cut-off adjustments, St George transactions, cyclone-related items, deferred cost of sale, loan and borrowing costs, trust-level accruals, and finally the NAV statement, dashboard, and distribution workings.

\subsection{Property Level (NAB-Sourced Entries)}

Property-level entries in Phase~2 fall into three categories based on their \textbf{source} and the \textbf{verification method} used to confirm their accuracy. Each category is described below with the source (where the data originates) and the reconciliation target (what it is checked against).

\subsubsection{Category A --- Source: Yardi TB Import \texorpdfstring{$\longrightarrow$}{->} Verified against: Yardi Export Data}

\textbf{What these are:} Balances that flow into the reporting pack \emph{directly from the Yardi TB import} (Step~5, Section~\ref{sec:yardi-import}). The Preparer does not post separate manual journals for Category~A items --- the import itself creates all GL movements. Verification means confirming that the imported figures in the reporting pack match the original Yardi export file.

\begin{itemize}[nosep]
    \item \textbf{Rental income and outgoings recovery (\acct{71.xx}):} Source = Yardi \texttt{cs4001} property-level export. Verify imported TB balances tie back to the Yardi export figures.
    \item \textbf{Property operating expenses (\acct{700.xx}):} Source = Yardi \texttt{cs4001}. Covers: property management, council rates, electricity, water, garden maintenance, cleaning, fire safety, and security. Verify imported amounts match Yardi export line by line.
    \item \textbf{Trade receivables (\acct{662} Debtors; \acct{663} Unallocated Income):} Source = Yardi. Verify imported balances against the Yardi Aged Receivables report.
    \item \textbf{Operating prepayments (\acct{706} --- Prepayments Operating; \acct{707} --- Prepayments Insurance):} Source = Yardi. Verify that the imported prepayment balances agree to the \textbf{Prepayments\_operating} tab schedule.
    \item \textbf{Operating accruals --- Yardi-originated (\acct{882.02}):} Source = Yardi (property-level accruals already recorded by CPG). Imported as part of the TB; no separate UFS manual entry required for these Yardi-originated accruals.
    \item \textbf{GST (\acct{255}):} Source = Yardi. Verify imported GST balance agrees to Yardi.
\end{itemize}

\subsubsection{Category B --- Source: NAB Bank Statement \texorpdfstring{$\longrightarrow$}{->} Verified against: Yardi vs.\ Bank Statement Reconciliation}

\textbf{What these are:} Entries where the Preparer must compare the NAB bank statement against the Yardi GL to identify and record cut-off timing differences. These are not imported from Yardi; they require manual journal entries posted by UFS. The reconciliation is performed in the \textbf{Yardi vs.\ Bank Stat Rec} tab and the \textbf{Cash} tab.

\begin{itemize}[nosep]
    \item \textbf{Cash --- NAB (\acct{685}):} Source = NAB bank statement (UFS Shared Folder). Reconcile the NAB bank statement closing balance to the per-books balance in the \textbf{Cash} tab. Any unexplained difference is investigated in the Yardi vs.\ Bank Statement reconciliation.
    \item \textbf{Cut-off Sundry Debtor entries (Cases~2--5):} Source = timing differences identified in Phase~1 Step~2 (Table~\ref{tab:fivecases}). For each Case~2--5 item, post the required Sundry Debtor journal entry --- refer to Step~3 (Section~\ref{sec:cutoff}).
    \item \textbf{Cyclone remediation capex (\acct{781.01}):} Source = NAB bank statement (cash payments made via NAB) cross-referenced against remediation invoices, which may be sourced from: (a)~\textbf{CPG SharePoint} (invoices uploaded by CPG: FHS, Premier Fire, Handler Property Group, etc.); (b)~\textbf{Yardi} (invoices attached to Yardi transactions and accessible within the Yardi system); or (c)~\textbf{CPG email/bank information request response} for any amounts not yet appearing in Yardi or SharePoint. Confirm each payment on the NAB bank statement and match to a supporting invoice before capitalising in the \textbf{Capex} tab. Do not expense through the P\&L.
\end{itemize}

\subsubsection{Category C --- Source: CPG Instructions, Invoices, or Schedules \texorpdfstring{$\longrightarrow$}{->} Verified against: Supporting Documentation (not Yardi or Bank Statement)}

\textbf{What these are:} Entries posted entirely by UFS based on CPG instructions, third-party invoices (from CPG SharePoint), or predetermined amortisation/accrual schedules. These do \emph{not} originate from the Yardi TB import and are \emph{not} reconciled to a bank statement. Their accuracy depends on the supporting document reviewed by the Preparer.

\begin{itemize}[nosep]
    \item \textbf{Operating accruals --- UFS-originated (\acct{882.02}):} Source = invoices received, CPG instruction, or historical patterns. Posted by UFS where a property-level obligation exists but has not yet been recorded in Yardi for the current period. Document the basis in the accrual workpaper.
    \item \textbf{Deferred cost of sale (\acct{709}):} Sale-related invoices may be sourced from: (a)~\textbf{CPG SharePoint} (primary location --- CPG uploads sale campaign invoices from CBRE, K\&L Gates, and MP Realty Trust); or (b)~\textbf{Yardi} (invoices may also be attached to Yardi transactions under the \texttt{cs4001} or \texttt{22chts} codes and should be checked in Yardi if a corresponding SharePoint document has not yet been received). Updated monthly in the \textbf{Receivables} tab. Do not expense while the sale is active; hold on balance sheet.
    \item \textbf{Prepaid leasing fee (\acct{780.12}) and fair value adjustment (\acct{780.30}):} Source = leasing invoices from Yardi or CPG SharePoint. Capitalised and amortised monthly per the \textbf{Prepaid leasing fee} tab.
    \item \textbf{Distribution payable (\acct{882.03}):} Source = CPG/client-approved distribution instruction. Record only upon receipt of written CPG approval; no estimate or unilateral accrual.
    \item \textbf{Capex fair value check:} Source = latest independent valuation report. Updated in the \textbf{Capex} tab to reconcile IP carrying value (\acct{780}) to the most recent independent valuation plus post-valuation capex additions.
\end{itemize}

\subsection{NAB Bank Statement Cut-Off Entries}
\label{sec:cutoff}

Using the reconciliation completed in Phase~1 Step~2 (Section~\ref{sec:yardi-rec}, Table~\ref{tab:fivecases}), the Preparer records cut-off entries as Sundry Debtors. Only Cases~2--5 require manual journal entries; Case~1 items are already captured through the imported Yardi TB (Step~5, Section~\ref{sec:yardi-import}).

\begin{note}
The five-case classification is defined once in Table~\ref{tab:fivecases} (Section~\ref{sec:yardi}) and applies identically to both the Yardi~vs.\ Bank Statement reconciliation and these cut-off journal entries. Do not create separate codes.
\end{note}

\subsection{St George Account Transactions}
\label{sec:stgeorge-entries}

Record all St George-related transactions per the St George bank statement (downloaded from CPG SharePoint). Interest charges and line fees are debited \emph{directly} from the St George facility account (\acct{680}) by the bank --- they do \textbf{not} flow through NAB (\acct{685}). Insurance claim proceeds and the sale deposit are also received into \acct{680}.

\begin{itemize}[nosep]
    \item \textbf{Interest expense} --- recorded to \acct{303.01} --- Loan Interest (\textbf{P\&L expense account}):
    \begin{itemize}[nosep]
        \item Recorded on a \textbf{cash basis} --- no month-end accrual is raised.
        \item When St George debits the facility: DR \acct{303.01} --- Loan Interest (P\&L) \; / \; CR \acct{680} --- St George.
        \item Confirm debit date and exact amount from the St George bank statement (downloaded from CPG SharePoint). Cross-reference against the \textbf{Loan\_St George} tab to verify the amount is consistent with the 1.95\% p.a.\ rate on the \$5,000,000 facility.
    \end{itemize}

    \item \textbf{Line fee} --- recorded to \acct{303.02} --- Line Fees (\textbf{P\&L expense account}):
    \begin{itemize}[nosep]
        \item Recorded on a \textbf{cash basis} --- no month-end accrual is raised.
        \item When St George debits the facility: DR \acct{303.02} --- Line Fees (P\&L) \; / \; CR \acct{680} --- St George.
        \item Confirm debit date and exact amount from the St George bank statement.
    \end{itemize}
    \item \textbf{Insurance claim proceeds received:} DR \acct{680} --- St George \; / \; CR \acct{73.02} --- Insurance Claim Income (proceeds credited directly to St George account by insurer; confirm via remittance advice from Steadfast IRS / Vision Re Partners).
    \item \textbf{Sale deposit received:} DR \acct{680} --- St George \; / \; CR \acct{884} --- Other Creditors (10\% deposit held as liability in St George account until unconditional settlement).
    \item \textbf{Other items} (e.g.\ bank facility fees): classify per nature and record accordingly.
\end{itemize}

\begin{note}
Interest expense (\acct{303.01}) and line fees (\acct{303.02}) are recorded on a \textbf{cash basis} --- no month-end accrual to \acct{882.16} is raised for either item. Both are settled via \acct{680} (St George facility), not via \acct{685} (NAB). The entry is posted directly when St George debits the facility: DR \acct{303.01} or \acct{303.02} (P\&L) / CR \acct{680} --- St George. NAB (\acct{685}) is not involved in interest or line fee settlement. Insurance \emph{expenses} (premiums) are paid via NAB (\acct{685}), whereas insurance claim \emph{proceeds} and interest/line fee debits all flow through St George (\acct{680}).
\end{note}

\subsection{Cyclone Insurance Claim and Remediation Capex}

\begin{enumerate}[nosep]
    \item Record insurance claim proceeds in \acct{73.02} (P\&L other income). Proceeds are received into \acct{680} --- St George (not NAB). Confirm amounts with remittance advice from Steadfast IRS / Vision Re Partners: DR \acct{680} --- St George / CR \acct{73.02} --- Insurance Claim Income.
    \item Insurance premium expenses are paid via NAB (\acct{685}) and appear on the NAB bank statement. Do not confuse with insurance claim receipts.
    \item Capitalise all remediation invoices to \acct{781.01} in the \textbf{Capex} tab (paid via NAB). Do not expense through the P\&L.
    \item Update Capex tab Fair Value Check: carrying value must reconcile to the latest independent valuation plus post-valuation capex.
    \item Accrue outstanding remediation invoices where an obligation exists.
\end{enumerate}

\subsection{Deferred Cost of Sale}

\begin{enumerate}[nosep]
    \item Review \acct{709} monthly on the \textbf{Receivables} tab; add new sale-related invoices.
    \item Do not amortise or expense while the sale is active.
    \item \textbf{If completed:} de-recognise \acct{709} against gain/loss on disposal.
    \item \textbf{If aborted:} expense to \acct{307} --- Aborted Sales Campaign Cost.
\end{enumerate}

\subsection{Trust Level (Loan and Borrowing Costs)}
\label{sec:borrowing-amort}

\begin{enumerate}[nosep]
    \item Record St George loan interest on a \textbf{cash basis} when St George debits the facility, per the \textbf{Loan\_St George} tab and the St George bank statement. No month-end accrual is raised:
    \begin{itemize}[nosep]
        \item DR \acct{303.01} --- Loan Interest (P\&L) \quad CR \acct{680} --- St George.
    \end{itemize}
    \item Record line fee on a \textbf{cash basis} when St George debits the facility, per the St George bank statement. No month-end accrual is raised:
    \begin{itemize}[nosep]
        \item DR \acct{303.02} --- Line Fees (P\&L) \quad CR \acct{680} --- St George.
    \end{itemize}
    \item Record monthly amortisation of prepaid borrowing costs on a straight-line basis over the remaining facility term --- \textbf{Borrowing cost prepaid} tab:
    \begin{itemize}[nosep]
        \item DR \acct{303.03} --- Establishment Fee Amortisation \quad CR \acct{708.03} --- Prepaid Establishment Fee.
        \item DR \acct{303.04} --- Legal Fee Amortisation \quad CR \acct{708.04} --- Prepaid Legal Fee.
    \end{itemize}
    \item Record CPG inter-group loan movements (\acct{882.08}) if applicable.
\end{enumerate}

\subsection{Trust-Level Accruals}
\label{sec:trust-accruals}

Record all Trust-level accruals in \acct{882.16} --- Fund Accruals. These are distinct from property-level operating accruals (\acct{882.02}). Standard items each period:

\textbf{Administration Costs (301):}
\begin{itemize}[nosep]
    \item DR \acct{301.01} --- Management Fees / CR \acct{882.16} --- 5\% of net receivable income (or per CPG invoice).
    \item DR \acct{301.02} --- Fund Admin \& Tax Fees / CR \acct{882.16} --- UFS fixed fee \$1,250/month (no CPI increase applied over the engagement).
    \item DR \acct{301.03} --- Registry Fees / CR \acct{882.16} --- per invoice or estimate.
    \item DR \acct{301.05} --- ASIC Fee / CR \acct{882.16} --- annual; accrue monthly or at year-end.
    \item DR \acct{301.10} --- Other Expenses / CR \acct{882.16} --- miscellaneous trust-level costs.
\end{itemize}

\textbf{Professional Fees (302):}
\begin{itemize}[nosep]
    \item DR \acct{302.02} --- Legal Fee / CR \acct{882.16} --- trust-level legal costs only (sale-related legal fees are capitalised to \acct{709}).
    \item DR \acct{302.03} --- Valuation Fee / CR \acct{882.16} --- independent valuation costs.
    \item DR \acct{302.04} --- Consultant Fee / CR \acct{882.16} --- per engagement.
    \item DR \acct{302.05} --- Audit Fee / CR \acct{882.16} --- accrue monthly or at period end.
\end{itemize}

\textbf{Conditional fees (sale in progress) --- require CPG confirmation before posting:}
\begin{itemize}[nosep]
    \item \textbf{Disposal Fee:} DR \acct{301.04} --- Disposal Fee / CR \acct{882.16} --- 1\% of GAV upon completion of sale.
    \item \textbf{Performance Fee:} DR \acct{303.05} --- Performance Fee / CR \acct{882.16} --- per Tier 1/Tier 2 structure (Section~\ref{sec:mgmtfee}). Accrue only when the performance threshold is probable.
\end{itemize}

\begin{note}
Account numbers \acct{301.04} (Disposal Fee) and \acct{303.05} (Performance Fee) are \textbf{reserved and maintained in the Chart of Accounts} even though neither fee is currently being accrued. Both fees are expected to be triggered upon completion of the property sale. The accounts will be activated once CPG confirms the applicable threshold has been met. Do not post to these accounts without CPG confirmation.
\end{note}

\subsection{NAV Statement}

Insert into the NAV Statement: General Ledger (\textbf{GL}), Balance Sheet (\textbf{BS}), Profit \& Loss (\textbf{PL}), and Cash Flow Statement (\textbf{CFS}).

\subsection{CPG Dashboard}

\textbf{Section 1 --- Operating Earnings and Distribution.}
\[
\text{OE} = \text{Net Ordinary Income} + \text{Depreciation} + \text{FV Adj.} + \text{Gain on Sale} - \text{Property Sales}
\]
Monthly OE = current month YTD $-$ prior month YTD. Insurance claim income (\acct{73.02}) flows through Net Ordinary Income; confirm with CPG whether separate disclosure is required.

\begin{note}
\textbf{Performance Fee is excluded from the Operating Earnings add-back.} Performance Fee is an expense to unitholders that directly reduces investor returns. Adding it back to OE would artificially inflate Operating Earnings and misrepresent the fund's distributable performance. Unlike non-cash items (depreciation, fair value adjustments) which are legitimately added back to reflect economic cash earnings, the Performance Fee represents a real economic cost borne by unitholders and must remain as a deduction. If the Performance Fee has been accrued, it is already captured as an expense within Net Ordinary Income and no further adjustment is required.
\end{note}

\textbf{Section 2 --- Balance Sheet.} Capital Contribution = \acct{500} (\$11,438,500). Debt = \acct{932} (\$5,000,000).
\[
\text{ICR} = \frac{\text{Net Property Income}}{\text{Interest Expenses}} \qquad \text{Gearing} = \frac{\text{Debt}}{\text{Total Assets}} \approx 36.8\%
\]

\textbf{Section 3 --- Unit Price.} Units on issue: 11,438,500. Unit Price = Net Asset / Units. NTA per unit = Adjusted NTA / Units.

\textbf{Section 4 --- Capex and Fees.} Capex from \textbf{Capex} tab; Management fee from \acct{301.01}; Leasing fees from \acct{700.26}.

\textbf{Section 5 --- Property Book Values.} IP value at month end (\acct{780} total: \$13,590,288 at January 2026). Most recent independent valuation: \$13,200,000 (31 December 2024).

\textbf{Section 6 --- Acquisitions/Divestments.} Update the Divestments row with exchange date, settlement date, and sale price when known.

\subsection{Distribution Workings}

Distribution is determined by CPG instruction. The Preparer prepares tax workings (refer: \textbf{Tax reconciliation}, \textbf{STI calc/Adj}, \textbf{Section 40--880/25--25}, \textbf{Tax depreciation} tabs). These are reviewed by both Reviewers, then sent to the Tax team. Distribution is recorded in \acct{882.03} only upon CPG/client approval.

% ============================================================================
\section{Phase 3: Internal Review and Client Distribution}
\label{sec:review}
% ============================================================================

\begin{enumerate}[nosep]
    \item The Preparer sends the completed pack to 1st and 2nd Reviewer via the UFS Shared Folder.
    \item Reviewers document comments; Preparer clears all comments before the pack advances.
    \item NAV pack and monthly report must be sent to CPG by \textbf{BD5}.
    \item The 1st Reviewer sends the approved pack to CPG for client review.
    \item CPG comments are addressed and resubmitted until approval is confirmed.
    \item Once CPG approves, the reporting pack is finalised and archived.
\end{enumerate}

% ============================================================================
\section{Checklists}
\label{sec:checklists}
% ============================================================================

All checklists are signed off by the 2nd Reviewer.

\subsection{Monthly NAV Procedures}

{\small\sffamily
\begin{longtable}{@{}C{0.6cm} L{10.2cm} L{2.5cm}@{}}
\caption{Monthly NAV procedures}\\
\rowcolor{navy}\textcolor{white}{\bfseries\#} & \textcolor{white}{\bfseries Procedural Item} & \textcolor{white}{\bfseries Responsibility} \\
\midrule
\endfirsthead
\rowcolor{navy}\textcolor{white}{\bfseries\#} & \textcolor{white}{\bfseries Procedural Item} & \textcolor{white}{\bfseries Responsibility} \\
\midrule
\endhead
\bottomrule
\endfoot

1 & NAB bank statement (current period) downloaded by Key Client Coordinator and archived in UFS Shared Folder & Client Coordinator \\
\rowcolor{warmgray} 2 & St George bank statement downloaded from CPG SharePoint & Preparer \\
3 & Yardi TB exports downloaded from Yardi (\texttt{cs4001} property-level; \texttt{22chts} trust-level) & Preparer \\
\rowcolor{warmgray} 4 & Yardi NAB TB vs.\ NAB bank statement reconciliation completed (\textbf{Yardi vs.\ Bank Stat Rec} tab) with narrative & Preparer \\
5 & Bank information request submitted to CPG (20th and BD1) & Preparer \\
\rowcolor{warmgray} 6 & All CPG SharePoint documents received (bank information responses, remediation invoices, insurance remittances, sale-related invoices) & Preparer \\
7 & Yardi TB revised: Trust-level expenses reclassified to \acct{882.16}; sale/leasing invoices reclassified per procedure & Preparer \\
\rowcolor{warmgray} 8 & Revised Yardi TB imported into Import\_Yardi tab & Preparer \\
9 & Cash reconciled: \acct{680} (St George), \acct{685} (NAB), \acct{686} (STA QLD) to bank statements & Preparer \\
\rowcolor{warmgray} 10 & Trade receivables (\acct{662}) and unallocated income (\acct{663}) reconciled & Preparer \\
11 & Deferred cost of sale (\acct{709}) updated with new sale-related invoices & Preparer \\
\rowcolor{warmgray} 12 & Insurance claim income (\acct{73.02}) recorded if receipt received (via St George \acct{680}) & Preparer \\
13 & Cyclone capex capitalised to \acct{781.01} in Capex tab (insurance expenses paid via NAB \acct{685}) & Preparer \\
\rowcolor{warmgray} 14 & Capex Fair Value Check updated (reconcile to latest independent valuation plus post-valuation capex) & Preparer \\
15 & Prepayments reconciled (\acct{706}, \acct{707}, \acct{708}) & Preparer \\
\rowcolor{warmgray} 16 & NAB cut-off bank statement entries recorded as Sundry Debtor (5 cases) & Preparer \\
17 & St George transactions recorded: interest, line fee, insurance claim, sale deposit & Preparer \\
\rowcolor{warmgray} 18 & Borrowing cost amortisation recorded (\acct{303.03}, \acct{303.04}) & Preparer \\
19 & Trust-level accruals recorded (\acct{882.16}): admin fee, registry, management fee, disposal fee if applicable & Preparer \\
\rowcolor{warmgray} 20 & Operating accruals recorded (\acct{882.02}) & Preparer \\
21 & CPG inter-group loan (\acct{882.08}) confirmed if applicable & Preparer \\
\rowcolor{warmgray} 22 & Distribution payable (\acct{882.03}) recorded if applicable & Preparer \\
23 & Dashboard KPIs linked and validated & Preparer \\
\rowcolor{warmgray} 24 & ICR calculated on 12-month rolling basis & Preparer \\
25 & NAV per unit calculated (unadjusted and adjusted NTA) & Preparer \\
\rowcolor{warmgray} 26 & GL, PL, BS, CFS inserted into NAV Statement & Preparer \\
27 & IP book value (\acct{780}) reconciled to latest independent valuation plus capex & Preparer \\
\rowcolor{warmgray} 28 & Lease schedule reviewed: tenant status, expiries, vacancy risk & Preparer \\
29 & St George maturity flagged if within 3 months & Preparer \\
\rowcolor{warmgray} 30 & Pack reviewed by 1st Reviewer; all comments cleared & 1st Reviewer \\
31 & Pack signed off by 2nd Reviewer & 2nd Reviewer \\
\rowcolor{warmgray} 32 & NAV pack and monthly report sent to CPG by BD5 & 1st Reviewer \\
\end{longtable}
}

\subsection{Quarterly BAS Procedures}

{\small\sffamily
\begin{longtable}{@{}C{0.6cm} L{10.2cm} L{2.5cm}@{}}
\caption{Quarterly BAS procedures}\\
\rowcolor{navy}\textcolor{white}{\bfseries\#} & \textcolor{white}{\bfseries Procedural Item} & \textcolor{white}{\bfseries Responsibility} \\
\midrule
\endfirsthead \endhead \bottomrule \endfoot

1 & GST ledger reviewed and reconciled for the quarter & Preparer \\
\rowcolor{warmgray} 2 & GST credits and output tax confirmed (incl.\ insurance GST) & Preparer \\
3 & BAS return workings reviewed by 1st Reviewer & 1st Reviewer \\
\rowcolor{warmgray} 4 & BAS lodged with ATO by due date & 1st / 2nd Reviewer \\
5 & BAS payment processed via NAB & CPG \\
\rowcolor{warmgray} 6 & BAS checklist signed off by 2nd Reviewer & 2nd Reviewer \\
\end{longtable}
}

\subsection{Quarterly Distribution Procedures}

{\small\sffamily
\begin{longtable}{@{}C{0.6cm} L{10.2cm} L{2.5cm}@{}}
\caption{Quarterly distribution procedures}\\
\rowcolor{navy}\textcolor{white}{\bfseries\#} & \textcolor{white}{\bfseries Procedural Item} & \textcolor{white}{\bfseries Responsibility} \\
\midrule
\endfirsthead \endhead \bottomrule \endfoot

1 & Tax reconciliation workings prepared (incl.\ insurance treatment) & Preparer \\
\rowcolor{warmgray} 2 & Tax workings reviewed by 1st and 2nd Reviewer & 1st / 2nd Reviewer \\
3 & Tax workings sent to Tax team for second review & 2nd Reviewer \\
\rowcolor{warmgray} 4 & Tax team confirms distribution components & Tax Team \\
5 & Components (cash, tax-deferred, capital return) sent to CPG & 1st Reviewer \\
\rowcolor{warmgray} 6 & CPG/client approval received & CPG \\
7 & Distribution recorded in \acct{882.03} and Unitholders tab & Preparer \\
\rowcolor{warmgray} 8 & Distribution checklist signed off by 2nd Reviewer & 2nd Reviewer \\
\end{longtable}
}

% ============================================================================
% APPENDIX A — PROCESS FLOWCHART  (Swim-Lane / Action-Document-Review Design)
% ============================================================================
\clearpage
\appendix
\section{Monthly Reporting Cycle --- Process Flowchart}
\label{app:flowchart}

Each numbered node corresponds to a step in Appendix~\ref{app:process-detail}.
Every action follows the control pattern: \textbf{Action~$\to$ Document~$\to$ Review~$\to$ Decision} (Yes = issues found, return to preparer; No = proceed).
Swim lanes indicate the responsible party.

% ============================================================================
% TIKZ STYLE DEFINITIONS
% ============================================================================
\tikzset{
  %% ---- Process / Action boxes (coloured by party) ----
  proc/.style={
    rectangle, rounded corners=4pt,
    draw=steel, line width=0.9pt, fill=palesky,
    font=\sffamily\fontsize{6.5}{8}\selectfont, minimum width=3.6cm, minimum height=1.2cm,
    align=center, text width=3.4cm, inner sep=3pt},
  proc/cpg/.style={
    rectangle, rounded corners=4pt,
    draw=critred!80, line width=0.9pt, fill=critbg,
    font=\sffamily\fontsize{6.5}{8}\selectfont, minimum width=3.6cm, minimum height=1.2cm,
    align=center, text width=3.4cm, inner sep=3pt},
  proc/rev/.style={
    rectangle, rounded corners=4pt,
    draw=infoteal, line width=0.9pt, fill=infobg,
    font=\sffamily\fontsize{6.5}{8}\selectfont, minimum width=3.6cm, minimum height=1.2cm,
    align=center, text width=3.4cm, inner sep=3pt},
  %% ---- Document boxes (sharp corners, gray fill) ----
  docn/.style={
    rectangle,
    draw=steel!50, line width=0.6pt, fill=warmgray,
    font=\sffamily\fontsize{5.5}{7}\selectfont,
    minimum width=3.0cm, minimum height=0.9cm,
    align=center, text width=2.8cm, inner sep=2pt},
  %% ---- Decision diamond ----
  dec/.style={
    diamond, aspect=2.2,
    draw=warnamber, line width=0.9pt, fill=warnbg,
    font=\sffamily\fontsize{6.5}{8}\selectfont,
    minimum width=2.0cm, align=center, inner sep=2pt},
  %% ---- Loop / fix helper box ----
  lbox/.style={
    rectangle, rounded corners=3pt,
    draw=textgray, line width=0.6pt, fill=warmgray,
    font=\sffamily\fontsize{5.5}{7}\selectfont,
    minimum width=2.2cm, minimum height=0.7cm,
    align=center, text width=2.0cm, inner sep=2pt},
  %% ---- Off-page connector (pentagon) ----
  opc/.style={
    regular polygon, regular polygon sides=5,
    shape border rotate=180,
    draw=navy, line width=0.9pt, fill=sky, text=navy,
    font=\sffamily\bfseries\normalsize,
    minimum size=0.8cm, align=center, inner sep=0pt},
  %% ---- Terminal (start / end) ----
  term/.style={
    rectangle, rounded corners=6pt,
    fill=navy, text=white,
    font=\sffamily\bfseries\small,
    minimum width=5cm, minimum height=0.65cm,
    align=center, inner sep=4pt},
  %% ---- Arrows & labels ----
  ar/.style={-Latex, draw=textgray, line width=0.8pt},
  lb/.style={font=\sffamily\fontsize{6}{7.5}\selectfont,
             fill=white, inner sep=1pt, text=textgray},
  %% ---- Swim-lane label ----
  lanelbl/.style={font=\sffamily\bfseries\footnotesize, text=white,
                  rotate=90, anchor=center},
}

%% ---- Process node macro: #1=step, #2=action, #3=person, #4=deadline ----
\newcommand{\PN}[4]{%
  {\fontsize{12}{14}\selectfont\bfseries\textcolor{navy}{#1}}\\[1pt]%
  {\fontsize{6}{7.5}\selectfont #2}\\[1pt]%
  {\fontsize{5}{6.5}\selectfont\textcolor{steel}{\textit{#3}}%
   \enspace\textbf{\textcolor{warnamber}{#4}}}%
}

%% ---- Document node macro: #1=document list ----
\newcommand{\DN}[1]{%
  {\fontsize{5.5}{6.5}\selectfont\textcolor{steel}{\textbf{Docs:}}}\\[1pt]%
  {\fontsize{5.5}{7}\selectfont #1}%
}

% ==========================================================================
%  PAGE 1 OF 5 — Phase 1a: Steps 1--3  (Source Documents & Reconciliation)
% ==========================================================================
\begin{landscape}
\vspace*{-0.4cm}
\begin{center}
{\sffamily\bfseries\large\textcolor{navy}{Phase 1a --- Source Document Collection \& Reconciliation (Steps 1--3)}}\par\vspace{0.25cm}

\resizebox{0.96\linewidth}{!}{%
\begin{tikzpicture}[every node/.style={font=\sffamily}]

%% ===== NODES =====

% -- START --
\node[term] (START) at (12,0.5) {MONTHLY REPORTING CYCLE --- BEGIN};

% -- CPG Lane: Step 1 --
\node[proc/cpg] (S1) at (4,-2.5) {\PN{1}{Upload source docs to CPG SharePoint}{CPG}{BD1}};
\node[docn]     (D1) at (10,-2.5) {\DN{St George bank stmt, bank info responses, invoices (remediation, insurance, sale) $\to$ SharePoint}};

% -- Coordinator Lane: Step 2 --
\node[proc]  (S2) at (4,-5.8) {\PN{2}{Download NAB bank stmt; archive in UFS Shared Folder}{Client Coord.}{20th \& BD1}};
\node[docn]  (D2) at (10,-5.8) {\DN{NAB bank stmt $\to$ UFS Shared Folder}};

% -- Preparer Lane: Step 3 --
\node[proc]  (S3) at (4,-9.5) {\PN{3}{Download Yardi TB exports; reconcile NAB TB vs bank stmt}{Preparer}{20th \& BD1}};
\node[docn]  (D3) at (10,-9.5) {\DN{cs4001, 22chts exports; Yardi vs Bank Stat Rec tab (5 cases)}};
\node[dec]   (R3) at (16,-9.5) {Rec balances\\to zero?};
\node[lbox]  (F3) at (16,-12.5) {Investigate \&\\resolve differences\\{\textit{Preparer}}};

% -- Off-page A --
\node[opc] (OA) at (21,-9.5) {A};
\node[lb, right=0.15cm of OA] {\textit{page 2}};

%% ===== SWIM-LANE BACKGROUNDS =====
\begin{scope}[on background layer]
  \fill[critbg!35]  (0.5,-1.2) rectangle (23,-4.2);
  \fill[palesky!25] (0.5,-4.2) rectangle (23,-7.5);
  \fill[palesky!12] (0.5,-7.5) rectangle (23,-13.5);
  \node[lanelbl, fill=critred!75, minimum width=3cm, minimum height=0.85cm,
        rounded corners=2pt] at (-0.3,-2.7) {CPG};
  \node[lanelbl, fill=steel, minimum width=3cm, minimum height=0.85cm,
        rounded corners=2pt] at (-0.3,-5.85) {Coordinator};
  \node[lanelbl, fill=steel!65, minimum width=6cm, minimum height=0.85cm,
        rounded corners=2pt] at (-0.3,-10.5) {Preparer};
  \draw[midgray, dashed, line width=0.35pt] (0.5,-4.2) -- (23,-4.2);
  \draw[midgray, dashed, line width=0.35pt] (0.5,-7.5) -- (23,-7.5);
\end{scope}

%% ===== ARROWS (all crossing-free) =====

% START -> S1 (down-left into CPG lane)
\draw[ar] (START.south) -- ++(0,-0.5) -| (S1.north);

% S1 -> D1 (right, within CPG lane)
\draw[ar] (S1.east) -- node[lb,above]{upload} (D1.west);

% D1 -> S2 (down from CPG doc to Coordinator action)
\draw[ar] (D1.south) |- (S2.north east);

% START -> S2 (parallel: Coordinator can start downloading NAB independently)
\draw[ar] (START.south) -- ++(0,-0.5) -| (S2.north);

% S2 -> D2 (right, within Coordinator lane)
\draw[ar] (S2.east) -- node[lb,above]{archive} (D2.west);

% D2 -> S3 (down from Coordinator doc to Preparer action)
\draw[ar] (D2.south) |- (S3.north east);

% S3 -> D3 (right, within Preparer lane)
\draw[ar] (S3.east) -- node[lb,above]{reconcile} (D3.west);

% D3 -> R3 (right, document to review gate)
\draw[ar] (D3.east) -- node[lb,above]{review} (R3.west);

% R3 -> No -> OA (right, proceed)
\draw[ar] (R3.east) -- node[lb,above]{No} (OA.west);

% R3 -> Yes -> F3 (down, issues found)
\draw[ar] (R3.south) -- node[lb,right]{Yes} (F3.north);

% F3 -> back to S3 (below all nodes, then up to S3 south)
\draw[ar] (F3.south) -- ++(0,-0.5) -| (S3.south);

\end{tikzpicture}
}%

\vspace{0.15cm}
{\small\sffamily
\textbf{Page 1 of 5}\enspace\textbullet\enspace
\colorbox{critbg}{\textcolor{critred}{\textbf{\ Step\ }}} CPG\quad
\colorbox{palesky}{\textcolor{steel}{\textbf{\ Step\ }}} Preparer / Coord.\quad
\colorbox{warmgray}{\textcolor{textgray}{\textbf{\ Doc\ }}} Document\quad
\colorbox{warnbg}{\textcolor{warnamber}{\textbf{$\diamond$}}} Decision\quad
\colorbox{sky}{\textcolor{navy}{\textbf{A}}} Off-page\quad
}
\end{center}
\end{landscape}

% ==========================================================================
%  PAGE 2 OF 5 — Phase 1b: Steps 4--6  (Bank Info Request & TB Import)
% ==========================================================================
\begin{landscape}
\vspace*{-0.4cm}
\begin{center}
{\sffamily\bfseries\large\textcolor{navy}{Phase 1b --- Bank Information Request \& TB Import (Steps 4--6)}}\par\vspace{0.25cm}

\resizebox{0.96\linewidth}{!}{%
\begin{tikzpicture}[every node/.style={font=\sffamily}]

%% ===== NODES =====

% -- Off-page A entry --
\node[opc] (OA) at (1,-5.5) {A};
\node[lb, left=0.1cm of OA] {\textit{from p.\,1}};

% -- Preparer Lane (upper): Step 4 --
\node[proc] (S4) at (5,-5.5) {\PN{4}{Prepare \& submit bank info request to CPG}{Preparer}{20th \& BD1}};
\node[docn] (D4) at (11,-5.5) {\DN{Bank info request template (Excel) sent to CPG}};

% -- CPG Lane: Step 5 --
\node[proc/cpg] (S5) at (5,-2.5) {\PN{5}{Respond to bank info; upload invoices to SharePoint}{CPG}{20th--BD1}};
\node[docn]     (D5) at (11,-2.5) {\DN{Invoices, remittances, bank info responses $\to$ SharePoint}};
\node[dec]      (R5) at (16.5,-2.5) {All info\\received?};
\node[lbox]     (F5) at (21,-2.5) {Follow up with\\CPG for outstanding\\items {\textit{Preparer}}};

% -- Sale/Loan confirm (risk gate within CPG lane) --
\node[dec]  (R5b) at (16.5,-5.5) {Sale / loan\\confirm\\needed?};
\node[lbox] (CF5) at (21,-5.5) {CPG confirms sale\\status + loan maturity\\position};

% -- Preparer Lane (lower): Step 6 --
\node[proc] (S6) at (5,-9.5) {\PN{6}{Revise Yardi TB (reclass trust / sale / leasing); import}{Preparer}{BD1}};
\node[docn] (D6) at (11,-9.5) {\DN{Yardi\_TB tab revised; Import\_Yardi tab updated}};
\node[dec]  (R6) at (16.5,-9.5) {TB import\\correct?};
\node[lbox] (F6) at (16.5,-12) {Fix reclassification\\errors\\{\textit{Preparer}}};

% -- Off-page B exit --
\node[opc] (OB) at (21,-9.5) {B};
\node[lb, right=0.1cm of OB] {\textit{page 3}};

%% ===== SWIM-LANE BACKGROUNDS =====
\begin{scope}[on background layer]
  \fill[critbg!35]  (0,-1.2) rectangle (23.5,-4.2);
  \fill[palesky!12] (0,-4.2) rectangle (23.5,-7.5);
  \fill[palesky!12] (0,-7.5) rectangle (23.5,-13);
  \node[lanelbl, fill=critred!75, minimum width=3cm, minimum height=0.85cm,
        rounded corners=2pt] at (-0.7,-2.7) {CPG};
  \node[lanelbl, fill=steel!65, minimum width=3.3cm, minimum height=0.85cm,
        rounded corners=2pt] at (-0.7,-5.85) {Preparer};
  \node[lanelbl, fill=steel!65, minimum width=5.5cm, minimum height=0.85cm,
        rounded corners=2pt] at (-0.7,-10.25) {Preparer};
  \draw[midgray, dashed, line width=0.35pt] (0,-4.2) -- (23.5,-4.2);
  \draw[midgray, dashed, line width=0.35pt] (0,-7.5) -- (23.5,-7.5);
\end{scope}

%% ===== ARROWS =====

% OA -> S4
\draw[ar] (OA.east) -- (S4.west);

% S4 -> D4 (right)
\draw[ar] (S4.east) -- node[lb,above]{prepare} (D4.west);

% D4 -> S5 (up into CPG lane: request sent)
\draw[ar] (D4.north) -- node[lb,right]{request sent} (S5.south);

% S5 -> D5 (right)
\draw[ar] (S5.east) -- node[lb,above]{respond} (D5.west);

% D5 -> R5 (right, review completeness)
\draw[ar] (D5.east) -- node[lb,above]{review} (R5.west);

% R5 -> Yes (issues) -> F5 (right)
\draw[ar] (R5.east) -- node[lb,above]{Yes} (F5.west);

% F5 -> back to S5 (loop above: go up then left then down)
\draw[ar] (F5.north) -- ++(0,0.8) -| (S5.north);

% R5 -> No -> R5b (down, proceed to sale/loan check)
\draw[ar] (R5.south) -- node[lb,right]{No} (R5b.north);

% R5b -> Yes -> CF5 (right, confirm needed)
\draw[ar] (R5b.east) -- node[lb,above]{Yes} (CF5.west);

% CF5 -> resolved (down to Step 6 area)
\draw[ar] (CF5.south) -- ++(0,-1.5) -| (D6.north east);

% R5b -> No -> down to S6 area
\draw[ar] (R5b.south) -- ++(0,-1.5) -| (S6.north east);

% D4 -> S6 (main flow: after sending request, continue to Step 6)
% Route: from D4 south edge, go down into Preparer lower lane
\draw[ar] (D4.south) -- ++(0,-1.5) -| (S6.north);

% S6 -> D6 (right)
\draw[ar] (S6.east) -- node[lb,above]{import} (D6.west);

% D6 -> R6 (right, review TB)
\draw[ar] (D6.east) -- node[lb,above]{review} (R6.west);

% R6 -> Yes -> F6 (down, issues found)
\draw[ar] (R6.south) -- node[lb,right]{Yes} (F6.north);

% F6 -> back to S6 (below then left then up)
\draw[ar] (F6.south) -- ++(0,-0.5) -| (S6.south);

% R6 -> No -> OB (right, proceed)
\draw[ar] (R6.east) -- node[lb,above]{No} (OB.west);

\end{tikzpicture}
}%

\vspace{0.15cm}
{\small\sffamily
\textbf{Page 2 of 5}\enspace\textbullet\enspace
\colorbox{critbg}{\textcolor{critred}{\textbf{\ Step\ }}} CPG\quad
\colorbox{palesky}{\textcolor{steel}{\textbf{\ Step\ }}} Preparer\quad
\colorbox{warmgray}{\textcolor{textgray}{\textbf{\ Doc\ }}} Document\quad
\colorbox{warnbg}{\textcolor{warnamber}{\textbf{$\diamond$}}} Decision / Risk Gate\quad
\colorbox{sky}{\textcolor{navy}{\textbf{A\,B}}} Off-page\quad
}
\end{center}
\end{landscape}

% ==========================================================================
%  PAGE 3 OF 5 — Phase 2a: Step 7 Sub-steps a--e (Property-Level Entries)
% ==========================================================================
\begin{landscape}
\vspace*{-0.4cm}
\begin{center}
{\sffamily\bfseries\large\textcolor{navy}{Phase 2a --- Reporting Pack Compilation: Property-Level (Steps 7a--7e)}}\par\vspace{0.25cm}

\resizebox{0.96\linewidth}{!}{%
\begin{tikzpicture}[every node/.style={font=\sffamily}]

%% ===== NODES (top-to-bottom flow, single Preparer lane) =====

% -- Off-page B entry --
\node[opc] (OB) at (1,-1.5) {B};
\node[lb, left=0.1cm of OB] {\textit{from p.\,2}};

% -- 7a: Property-level entries (Cat A/B/C) --
\node[proc] (S7a) at (5.5,-1.5) {\PN{7a}{Record property-level entries (Categories A / B / C)}{Preparer}{BD2}};
\node[docn] (D7a) at (12,-1.5) {\DN{Import\_Yardi, Receivables, Cash, Prepayments tabs verified}};

% -- 7b: NAB cut-off (connected from 7a) --
\node[proc] (S7b) at (5.5,-4.5) {\PN{7b}{NAB cut-off Sundry Debtor entries (Cases 2--5)}{Preparer}{BD2}};
\node[docn] (D7b) at (12,-4.5) {\DN{Yardi vs Bank Rec tab; Sundry Debtor journals posted}};
\node[dec]  (R7b) at (18,-4.5) {Rec\\balances?};
\node[lbox] (F7b) at (18,-7) {Resolve unmatched\\items; re-check\\5-case coding};

% -- 7c: St George interest + line fee --
\node[proc] (S7c) at (5.5,-8) {\PN{7c}{Record StG interest (303.01) \& line fee (303.02) --- cash basis}{Preparer}{BD2--3}};
\node[docn] (D7c) at (12,-8) {\DN{Loan\_StG tab; StG bank stmt (from SharePoint)}};

% -- 7d: Insurance claim + cyclone capex --
\node[proc] (S7d) at (5.5,-10.8) {\PN{7d}{Insurance claim income (73.02); cyclone capex (781.01)}{Preparer}{BD3}};
\node[docn] (D7d) at (12,-10.8) {\DN{Capex tab; StG stmt (claim receipts); remittance advice; NAB stmt (capex pmts)}};
\node[dec]  (R7d) at (18,-10.8) {Capex FV\\check OK?};
\node[lbox] (F7d) at (18,-13) {Update carrying\\value to valuation\\+ post-val capex};

% -- 7e: Deferred cost of sale --
\node[proc] (S7e) at (5.5,-14) {\PN{7e}{Update deferred cost of sale (709) from new invoices}{Preparer}{BD3}};
\node[docn] (D7e) at (12,-14) {\DN{Receivables tab; SharePoint / Yardi sale invoices (CBRE, K\&L Gates, MP Realty)}};

% -- Off-page C exit --
\node[opc] (OC) at (22,-14) {C};
\node[lb, right=0.1cm of OC] {\textit{page 4}};

%% ===== SWIM-LANE BACKGROUND =====
\begin{scope}[on background layer]
  \fill[palesky!12] (0,-0.2) rectangle (24,-15.3);
  \node[lanelbl, fill=steel!65, minimum width=15.1cm, minimum height=0.85cm,
        rounded corners=2pt] at (-0.7,-7.75) {\textcolor{white}{Preparer --- Step 7 Compilation (Property-Level)}};
\end{scope}

%% ===== ARROWS =====

% Entry -> 7a
\draw[ar] (OB.east) -- (S7a.west);

% Vertical spine: draw a line down the left side from entry level for independent branches
\draw[steel!40, line width=0.6pt, dashed] ([xshift=-1.5cm]S7a.west) -- ++(0,-12.5);

% Spine -> 7c branch point (horizontal stub already drawn below)
\draw[ar] (OB.south) -- ++(0,-6.5) -| ([xshift=-1.5cm]S7c.west);

% Spine -> 7d branch point
\draw[ar] (OB.south) -- ++(0,-9.3) -| ([xshift=-1.5cm]S7d.west);

% Spine -> 7e branch point
\draw[ar] (OB.south) -- ++(0,-12.5) -| ([xshift=-1.5cm]S7e.west);

% 7a flow: action -> doc
\draw[ar] (S7a.east) -- node[lb,above]{verify} (D7a.west);

% 7a -> 7b (connected: both NAB-related)
\draw[ar] (D7a.south) |- (S7b.north east);
\draw[ar] (S7a.south) -- (S7b.north);

% 7b flow: action -> doc -> review
\draw[ar] (S7b.east) -- node[lb,above]{post} (D7b.west);
\draw[ar] (D7b.east) -- node[lb,above]{review} (R7b.west);

% R7b Yes -> F7b -> back to S7b
\draw[ar] (R7b.south) -- node[lb,right]{Yes} (F7b.north);
\draw[ar] (F7b.south) -- ++(0,-0.5) -| (S7b.south);

% R7b No -> down to 7c area (route right then down to avoid crossing D7c)
\draw[ar] (R7b.east) -- ++(2.5,0) |- (D7c.east);

% 7b -> 7c: INDEPENDENT — no sequential arrow (St George is separate from NAB cut-off)
% Entry spine branches to 7c directly
\draw[ar] ([xshift=-1.5cm]S7c.west) -- (S7c.west);

% 7c flow: action -> doc
\draw[ar] (S7c.east) -- node[lb,above]{record} (D7c.west);

% 7c -> 7d: INDEPENDENT — no sequential arrow (insurance capex is separate from loan interest)
% Entry spine branches to 7d directly
\draw[ar] ([xshift=-1.5cm]S7d.west) -- (S7d.west);

% 7d flow: action -> doc -> review
\draw[ar] (S7d.east) -- node[lb,above]{capitalise} (D7d.west);
\draw[ar] (D7d.east) -- node[lb,above]{review} (R7d.west);

% R7d Yes -> F7d -> back to S7d
\draw[ar] (R7d.south) -- node[lb,right]{Yes} (F7d.north);
\draw[ar] (F7d.south) -- ++(0,-0.5) -| (S7d.south);

% R7d No -> proceed
\draw[ar] (R7d.east) -- ++(1.5,0) |- (OC.north);

% 7d -> 7e: INDEPENDENT — no sequential arrow (deferred cost of sale is separate)
% Entry spine branches to 7e directly
\draw[ar] ([xshift=-1.5cm]S7e.west) -- (S7e.west);

% 7e flow: action -> doc
\draw[ar] (S7e.east) -- node[lb,above]{update} (D7e.west);

% 7e -> Off-page C
\draw[ar] (D7e.east) -- (OC.west);

\end{tikzpicture}
}%

\vspace{0.15cm}
{\small\sffamily
\textbf{Page 3 of 5}\enspace\textbullet\enspace
\colorbox{palesky}{\textcolor{steel}{\textbf{\ Step\ }}} Preparer\quad
\colorbox{warmgray}{\textcolor{textgray}{\textbf{\ Doc\ }}} Document\quad
\colorbox{warnbg}{\textcolor{warnamber}{\textbf{$\diamond$}}} Decision\quad
\colorbox{sky}{\textcolor{navy}{\textbf{B\,C}}} Off-page\quad
Sub-steps 7a--7e cover property-level entries.
Arrows between 7a$\to$7b reflect NAB data dependency.
}
\end{center}
\end{landscape}

% ==========================================================================
%  PAGE 4 OF 5 — Phase 2b: Step 7 Sub-steps f--j (Trust-Level & Outputs)
% ==========================================================================
\begin{landscape}
\vspace*{-0.4cm}
\begin{center}
{\sffamily\bfseries\large\textcolor{navy}{Phase 2b --- Reporting Pack Compilation: Trust-Level \& Outputs (Steps 7f--7j)}}\par\vspace{0.25cm}

\resizebox{0.96\linewidth}{!}{%
\begin{tikzpicture}[every node/.style={font=\sffamily}]

%% ===== NODES =====

% -- Off-page C entry --
\node[opc] (OC) at (1,-1.5) {C};
\node[lb, left=0.1cm of OC] {\textit{from p.\,3}};

% -- 7f: Borrowing cost amortisation (linked from 7c: loan-related) --
\node[proc] (S7f) at (5.5,-1.5) {\PN{7f}{Borrowing cost amortisation (303.03, 303.04)}{Preparer}{BD3}};
\node[docn] (D7f) at (12,-1.5) {\DN{Borrowing cost prepaid tab; straight-line schedule}};

% -- 7g: Trust-level accruals --
\node[proc] (S7g) at (5.5,-4.3) {\PN{7g}{Trust-level accruals (882.16) \& operating accruals (882.02)}{Preparer}{BD3}};
\node[docn] (D7g) at (12,-4.3) {\DN{Accruals tab; CPG invoices; contracts; prior-period patterns}};
\node[dec]  (R7g) at (18,-4.3) {Accrual\\support?};
\node[lbox] (F7g) at (18,-6.8) {Obtain missing\\invoices / CPG\\confirmation};

% -- 7h: Inter-group loan + distribution (linked from 7g) --
\node[proc] (S7h) at (5.5,-7.8) {\PN{7h}{Inter-group loan (882.08) \& distribution payable (882.03)}{Preparer}{BD3}};
\node[docn] (D7h) at (12,-7.8) {\DN{Unitholders tab; CPG written approval required for distribution}};

% -- 7i: NAV, Dashboard, ICR, unit price (depends on all above) --
\node[proc] (S7i) at (5.5,-10.5) {\PN{7i}{NAV Statement, Dashboard, ICR, unit price}{Preparer}{BD4}};
\node[docn] (D7i) at (12,-10.5) {\DN{NAV per unit, Dashboard, GL, PL, BS, CFS tabs; OE formula check}};

% -- 7j: Lease review + IP check + loan flag --
\node[proc] (S7j) at (5.5,-13.2) {\PN{7j}{Lease review, IP book value check, loan maturity flag}{Preparer}{BD4}};
\node[docn] (D7j) at (12,-13.2) {\DN{Capex tab (IP vs valuation); lease schedule; StG maturity flag}};

% -- Self-review gate --
\node[dec]  (SR) at (18,-13.2) {Self-review:\\all tabs\\complete?};
\node[lbox] (FSR) at (18,-15.8) {Identify gaps \&\\complete entries\\{\textit{Preparer}}};

% -- Off-page D exit --
\node[opc] (OD) at (22,-13.2) {D};
\node[lb, right=0.1cm of OD] {\textit{page 5}};

%% ===== SWIM-LANE BACKGROUND =====
\begin{scope}[on background layer]
  \fill[palesky!12] (0,-0.2) rectangle (24,-16.5);
  \node[lanelbl, fill=steel!65, minimum width=16.3cm, minimum height=0.85cm,
        rounded corners=2pt] at (-0.7,-8.35) {\textcolor{white}{Preparer --- Step 7 Compilation (Trust-Level \& Final Outputs)}};
\end{scope}

%% ===== ARROWS =====

% Entry -> 7f
\draw[ar] (OC.east) -- (S7f.west);

% 7f flow
\draw[ar] (S7f.east) -- node[lb,above]{amortise} (D7f.west);

% 7f -> 7g: INDEPENDENT — no sequential arrow (borrowing amortisation is separate from accruals)
% Entry spine branches to 7g directly
\draw[ar] (OC.south) -- ++(0,-2.8) -| ([xshift=-1.5cm]S7g.west);
\draw[ar] ([xshift=-1.5cm]S7g.west) -- (S7g.west);

% 7g flow: action -> doc -> review
\draw[ar] (S7g.east) -- node[lb,above]{post} (D7g.west);
\draw[ar] (D7g.east) -- node[lb,above]{review} (R7g.west);

% R7g Yes -> F7g -> back to S7g
\draw[ar] (R7g.south) -- node[lb,right]{Yes} (F7g.north);
\draw[ar] (F7g.south) -- ++(0,-0.5) -| (S7g.south);

% R7g No -> proceed down (route right to avoid crossing D7h)
\draw[ar] (R7g.east) -- ++(2.5,0) |- (D7h.east);

% 7g -> 7h (connected: accruals feed distribution)
\draw[ar] (S7g.south) -- (S7h.north);

% 7h flow
\draw[ar] (S7h.east) -- node[lb,above]{record} (D7h.west);

% 7h -> 7i (sequential)
\draw[ar] (S7h.south) -- ++(0,-0.3) -- (S7i.north);

% 7f doc -> 7i (loan costs feed into NAV: connection from above)
\draw[ar] (D7f.south) -- ++(0,-0.5) -| ([xshift=-0.5cm]S7i.north);

% 7i flow
\draw[ar] (S7i.east) -- node[lb,above]{compile} (D7i.west);

% 7i -> 7j (sequential)
\draw[ar] (S7i.south) -- (S7j.north);

% 7j flow: action -> doc -> self-review
\draw[ar] (S7j.east) -- node[lb,above]{check} (D7j.west);
\draw[ar] (D7j.east) -- node[lb,above]{review} (SR.west);

% SR Yes -> FSR -> back to S7i (re-check from outputs level)
\draw[ar] (SR.south) -- node[lb,right]{Yes} (FSR.north);
\draw[ar] (FSR.south) -- ++(0,-0.5) -| (S7j.south);

% SR No -> OD (proceed to Phase 3)
\draw[ar] (SR.east) -- node[lb,above]{No} (OD.west);

\end{tikzpicture}
}%

\vspace{0.15cm}
{\small\sffamily
\textbf{Page 4 of 5}\enspace\textbullet\enspace
\colorbox{palesky}{\textcolor{steel}{\textbf{\ Step\ }}} Preparer\quad
\colorbox{warmgray}{\textcolor{textgray}{\textbf{\ Doc\ }}} Document\quad
\colorbox{warnbg}{\textcolor{warnamber}{\textbf{$\diamond$}}} Decision\quad
\colorbox{sky}{\textcolor{navy}{\textbf{C\,D}}} Off-page\quad
Sub-steps 7f--7j cover trust-level entries and final outputs.
7f connects from 7c (loan-related); 7g$\to$7h (accruals$\to$distribution); all$\to$7i (NAV compilation).
}
\end{center}
\end{landscape}

% ==========================================================================
%  PAGE 5 OF 5 — Phase 3: Steps 8--10  (Review & Client Distribution)
% ==========================================================================
\begin{landscape}
\vspace*{-0.4cm}
\begin{center}
{\sffamily\bfseries\large\textcolor{navy}{Phase 3 --- Internal Review \& Client Distribution (Steps 8--10)}}\par\vspace{0.25cm}

\resizebox{0.96\linewidth}{!}{%
\begin{tikzpicture}[every node/.style={font=\sffamily}]

%% ===== NODES =====

% -- Off-page D entry --
\node[opc] (OD) at (1,-3.5) {D};
\node[lb, left=0.1cm of OD] {\textit{from p.\,4}};

% -- Preparer Lane: Step 8 --
\node[proc] (S8) at (5.5,-3.5) {\PN{8}{Send completed pack to 1st \& 2nd Reviewer}{Preparer}{BD4}};
\node[docn] (D8) at (12,-3.5) {\DN{Full reporting workbook via UFS Shared Folder}};

% -- Reviewer Lane: Step 9 --
\node[proc/rev] (S9) at (5.5,-7) {\PN{9}{Review pack independently; document comments}{1st \& 2nd Reviewer}{BD5}};
\node[docn]     (D9) at (12,-7) {\DN{NAV checklist, BAS checklist, Distribution checklist signed}};
\node[dec]      (R9a) at (18,-3.5) {Reviewer\\comments?};
\node[lbox]     (CLR) at (22,-3.5) {Preparer clears\\all comments;\\re-submits pack};
\node[dec]      (R9b) at (18,-7) {All checks\\pass?};
\node[lbox]     (RET) at (22,-7) {Return to Preparer\\to address failed\\items};

% -- Step 10: Send to CPG --
\node[proc/rev] (S10) at (5.5,-10.5) {\PN{10}{Send approved NAV pack \& monthly report to CPG}{1st Reviewer}{BD5}};
\node[docn]     (D10) at (12,-10.5) {\DN{NAV pack, monthly report sent to CPG}};
\node[dec]      (R10) at (18,-10.5) {CPG\\comments?};
\node[lbox]     (RESUB) at (22,-10.5) {Address CPG\\comments; resubmit\\revised pack};

% -- Archive --
\node[proc, minimum width=3.6cm] (ARC) at (12,-13.5) {\PN{}{Archive CPG-approved pack in UFS Shared Folder}{1st Reviewer}{BD5}};
\node[docn] (DARC) at (18,-13.5) {\DN{Final approved pack archived in UFS Shared Folder}};

% -- END --
\node[term, minimum width=7cm] (END) at (12,-15.5) {MONTHLY REPORTING CYCLE --- COMPLETE};

%% ===== SWIM-LANE BACKGROUNDS =====
\begin{scope}[on background layer]
  \fill[palesky!12] (0,-2) rectangle (24.5,-5.2);
  \fill[infobg!25]  (0,-5.2) rectangle (24.5,-9);
  \fill[infobg!25]  (0,-9) rectangle (24.5,-12);
  \fill[critbg!20]  (0,-12) rectangle (24.5,-14.8);
  \fill[palesky!8]  (0,-14.8) rectangle (24.5,-16.2);
  \node[lanelbl, fill=steel!65, minimum width=3.2cm, minimum height=0.85cm,
        rounded corners=2pt] at (-0.7,-3.6) {Preparer};
  \node[lanelbl, fill=infoteal, minimum width=3.8cm, minimum height=0.85cm,
        rounded corners=2pt] at (-0.7,-7.1) {1st and 2nd Reviewer};
  \node[lanelbl, fill=infoteal!80, minimum width=3.8cm, minimum height=0.85cm,
        rounded corners=2pt] at (-0.7,-10.5) {1st and 2nd Reviewer};
  \node[lanelbl, fill=critred!60, minimum width=2.8cm, minimum height=0.85cm,
        rounded corners=2pt] at (-0.7,-13.4) {CPG / Archive};
  \draw[midgray, dashed, line width=0.35pt] (0,-5.2) -- (24.5,-5.2);
  \draw[midgray, dashed, line width=0.35pt] (0,-9)   -- (24.5,-9);
  \draw[midgray, dashed, line width=0.35pt] (0,-12)  -- (24.5,-12);
  \draw[midgray, dashed, line width=0.35pt] (0,-14.8)-- (24.5,-14.8);
\end{scope}

%% ===== ARROWS =====

% Entry -> S8
\draw[ar] (OD.east) -- (S8.west);

% S8 -> D8 (submit pack)
\draw[ar] (S8.east) -- node[lb,above]{submit} (D8.west);

% D8 -> R9a (review gate: are there comments?)
\draw[ar] (D8.east) -- node[lb,above]{review} (R9a.west);

% R9a Yes -> CLR (comments found, clear them)
\draw[ar] (R9a.east) -- node[lb,above]{Yes} (CLR.west);

% CLR -> back to S8 (go up then left to S8 top)
\draw[ar] (CLR.north) -- ++(0,0.8) -| (S8.north);

% R9a No -> S9 (no comments pending, proceed to formal review)
\draw[ar] (R9a.south) -- node[lb,right]{No} (S9.north east);

% S9 -> D9 (review and sign checklists)
\draw[ar] (S9.east) -- node[lb,above]{sign off} (D9.west);

% D9 -> R9b (all checks pass?)
\draw[ar] (D9.east) -- node[lb,above]{review} (R9b.west);

% R9b Fail -> RET (return to Preparer)
\draw[ar] (R9b.east) -- node[lb,above]{Fail} (RET.west);

% RET -> back to S8 (go up then left)
\draw[ar] (RET.north) -- ++(0,2.2) -| ([xshift=0.5cm]S8.north);

% R9b Pass -> S10 (proceed to client distribution)
\draw[ar] (R9b.south) -- node[lb,right]{Pass} (S10.north east);

% S10 -> D10 (send to CPG)
\draw[ar] (S10.east) -- node[lb,above]{send} (D10.west);

% D10 -> R10 (CPG comments?)
\draw[ar] (D10.east) -- node[lb,above]{review} (R10.west);

% R10 Yes -> RESUB (CPG has comments)
\draw[ar] (R10.east) -- node[lb,above]{Yes} (RESUB.west);

% RESUB -> back to S10 (go down then left then up)
\draw[ar] (RESUB.south) -- ++(0,-0.8) -| (S10.south);

% R10 No -> ARC (CPG approved, archive)
\draw[ar] (R10.south) -- node[lb,right]{No} (ARC.north east);

% ARC -> DARC
\draw[ar] (ARC.east) -- node[lb,above]{archive} (DARC.west);

% ARC -> END
\draw[ar] (ARC.south) -- (END.north);

\end{tikzpicture}
}%

\vspace{0.15cm}
{\small\sffamily
\textbf{Page 5 of 5}\enspace\textbullet\enspace
\colorbox{critbg}{\textcolor{critred}{\textbf{\ Step\ }}} CPG\quad
\colorbox{palesky}{\textcolor{steel}{\textbf{\ Step\ }}} Preparer\quad
\colorbox{infobg}{\textcolor{infoteal}{\textbf{\ Step\ }}} 1st and 2nd Reviewer\quad
\colorbox{warmgray}{\textcolor{textgray}{\textbf{\ Doc\ }}} Document\quad
\colorbox{warnbg}{\textcolor{warnamber}{\textbf{$\diamond$}}} Decision / Risk Gate\quad
\colorbox{sky}{\textcolor{navy}{\textbf{D}}} Off-page\quad
}
\end{center}
\end{landscape}

% ============================================================================
\clearpage
\section{Detailed Process Action Narratives}
\label{app:process-detail}

This section provides the full narrative for each step, as referenced in the flowchart in Appendix~\ref{app:flowchart}.

\subsection*{Step 1 — CPG: Document Upload (BD1)}
CPG uploads the St George bank statement, bank information responses, and all supporting invoices (remediation, insurance, sale-related) to the designated CPG SharePoint location for Preparer access.

\subsection*{Step 2 — Key Client Coordinator: NAB Statement (20th \& BD1)}
Downloads the NAB bank statement from NAB online banking. Archives it in the Trust's folder on the UFS Shared Folder for Preparer access.

\subsection*{Step 3 — Preparer: Yardi Import and Bank Reconciliation (20th \& BD1)}
Downloads both Yardi TB movement exports from the Yardi system (\texttt{cs4001} and \texttt{22chts}). Downloads the St George bank statement from SharePoint. Reconciles the Yardi NAB TB against the NAB bank statement in the \textbf{Yardi vs.\ Bank Stat Rec} tab using the five-case classification (see Table~\ref{tab:fivecases}). The reconciliation must balance to zero before proceeding.

\subsection*{Step 4 — Preparer: Bank Information Request (20th \& BD1)}
Prepares and submits a bank information request to CPG covering all unidentified or unmatched transactions. Queries cover: missing invoices, unidentified payments, cut-off items, insurance claim remittances, sale invoices.

\subsection*{Step 5 — CPG: Invoice and Information Responses (20th to BD1)}
Provides written responses to bank information requests. Uploads all supporting invoices and remittance advices to CPG SharePoint. Confirms sale status and loan maturity position if requested.

\subsection*{Step 6 — Preparer: Yardi TB Revision and Import (BD1)}
Reviews the raw Yardi TB; reclassifies trust-level expenses from P\&L to \acct{882.16}; reclassifies sale-related invoices to \acct{709} and leasing invoices to \acct{780.12}. Imports the revised TB into the \textbf{Import\_Yardi} tab.

\subsection*{Step 7 — Preparer: Full Reporting Pack Compilation (BD2--BD4)}
Compiles the full reporting pack. Sub-steps 7a--7j follow the recommended order:
\begin{enumerate}[nosep,label=(\alph*)]
  \item Property-level entries (Categories A/B/C);
  \item NAB cut-off Sundry Debtor entries (Cases 2--5);
  \item St George interest (\acct{303.01}) and line fee (\acct{303.02}) on a cash basis when debited from the facility --- no month-end accrual raised for either item;
  \item Insurance claim income (\acct{73.02}) and cyclone capex (\acct{781.01});
  \item Deferred cost of sale (\acct{709}) per invoices from SharePoint or Yardi;
  \item Borrowing cost amortisation (\acct{303.03}, \acct{303.04});
  \item Trust-level accruals (\acct{882.16}) and operating accruals (\acct{882.02});
  \item CPG inter-group loan (\acct{882.08}) and distribution payable (\acct{882.03}) if applicable;
  \item NAV Statement, Dashboard, ICR, unit price;
  \item Lease review, IP book value check, and St George loan maturity flag.
\end{enumerate}

\subsection*{Step 8 — Preparer: Pack Submission for Review (BD4)}
Sends the completed pack to the 1st Reviewer and 2nd Reviewer via the UFS Shared Folder. Clears all review comments before the pack advances to sign-off.

\subsection*{Step 9 — 1st and 2nd Reviewer: Review and Sign-Off (BD5)}
Both Reviewers review the pack independently. Document comments; Preparer clears. 2nd Reviewer signs off all checklists. Reviewers confirm: all balances reconcile, accruals are supported, P\&L items correctly classified, OE formula excludes Performance Fee, and loan maturity flag is current.

\subsection*{Step 10 — 1st Reviewer: Client Distribution (BD5)}
Sends the approved NAV pack and monthly report to CPG by BD5. Addresses any CPG comments; resubmits until CPG approval is confirmed. Archives the final pack in the UFS Shared Folder.

\vfill
\begin{center}
\textcolor{navy}{\rule{6cm}{0.5pt}}\\[0.6em]
{\sffamily\large\bfseries --- End of Document ---}
\end{center}

\end{document}
